---
title: "SB GAM stratified by sex, maternal nationality, SSEP or Language Region"
author: "Mathilde Le Vu"
date:  "`r Sys.Date()`"
html_document: 
output:
  rmdformats::robobook:
    code_folding: show
    self_contained: true
    highlight: pygments
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Socio economic position : stratification
## PTB % by SSEP tertile, unadjusted
```{r}
table(bevn_eco_in7$mean_ssep2_cat1, bevn_eco_in7$PTB, useNA="always")
round(prop.table(table(bevn_eco_in7$mean_ssep2_cat1, bevn_eco_in7$PTB, useNA="always"), margin=1)*100,2)
```

## PTB % stratified by SSEP tertile, adjusted for all covariates
```{r include=FALSE}
m_SB_bam_L_SSEP1_2 <- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_L_SSEP1)  
m_SB_bam_M_SSEP1_2 <- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_M_SSEP1)  
m_SB_bam_H_SSEP1_2 <- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_H_SSEP1)

#function to extract the plot information
plot_m_SB_bam_L_SSEP1_2 <- GAM_plot_function_binary(m_SB_bam_L_SSEP1_2, 1) %>%
  mutate(SEP="low")
plot_m_SB_bam_M_SSEP1_2 <- GAM_plot_function_binary(m_SB_bam_M_SSEP1_2, 1) %>%
  mutate(SEP="medium")
plot_m_SB_bam_H_SSEP1_2 <- GAM_plot_function_binary(m_SB_bam_H_SSEP1_2, 1) %>%
  mutate(SEP="high")
```

```{r}
x_date <-   bevn_eco_in6 %>% #careful, mayhave to change the dataset if I later work with smaller time ranges!
  select(birth_Y_M, birth_Y_M_num) %>%
  distinct(birth_Y_M, .keep_all = TRUE) %>%
  rename(x=birth_Y_M_num)

plot_SB_SEP2 <- plot_m_SB_bam_L_SSEP1_2  %>%
  rbind(plot_m_SB_bam_M_SSEP1_2) %>%
  rbind(plot_m_SB_bam_H_SSEP1_2) %>%
  mutate(x=round(x,0)) %>%
  left_join(x_date) %>%
  mutate(date_x= ymd(paste0(birth_Y_M,"-01")))

# graph parameters: 
lim1 <- as.POSIXct(ymd("2007-01-01"))
lim2 <- as.POSIXct(ymd("2022-12-01"))

ggplot_SB_SEP2 <- ggplot(data=plot_SB_SEP2)+
  geom_line(aes(x=as.POSIXct(date_x),y=fit,col=SEP, linetype=SEP),lwd=lwdline)+
  geom_ribbon(aes(x=as.POSIXct(date_x),ymin=CIl,ymax=CIu,fill=SEP),alpha=0.15,lwd=lwdline)+
  xlab("Timeline (years)")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.001,0.007)) +
  # scale_colour_manual("",
  #                     values = c("#555555","#555555","#555555"),
  #                     limits=c("fitall","CIlall","CIuall"),
  #                     labels=c("fully adjusted","95% CI","95% CI"))+
  scale_colour_manual('SSEP',                                                #colour manual is for the line
                      limits=c("low","medium", "high"),
                      # labels=c("fully adjusted","95% CI","95% CI"),
                    values =c("darkorchid1","lightpink3", "darkmagenta"))+
  scale_fill_manual('SSEP',                                              # fill is for CI
                    limits=c("low","medium", "high"), 
                    # labels=c("fully adjusted","95% CI","95% CI"),  
                    values =c("darkorchid1","lightpink3", "darkmagenta"))+
  scale_x_datetime( breaks = date_breaks("12 month"), 
                    labels = label_date_short(),
                    limits =c(as.POSIXct("2007-01-01"), max(lim2)),
                    expand = c(0,0)) +
  scale_linetype_manual('SSEP',
                        limits = c("low", "medium", "high"),
                        values = c("solid", "dashed", "dotted")) +
    theme_bw()+
  theme(axis.text.y=element_text(color="black",size=10),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        axis.title.y=element_text(size=14), # Decrease y-axis title font size
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom",
        legend.key.width = unit(1.5, "cm"), 
        legend.key.height = unit(0.5, "cm")
        #,    panel.grid.major=element_line(colour = "black", linetype = "dotted"),
   # panel.grid.minor=element_line(colour = "black", linetype = "dotted")
   ) +
theme(axis.title.x = axis.title.x.position)
ggplot_SB_SEP2
# 
# save(ggplot_PTB_SEP2, file='output/figures_paper/ggplot_PTB_SEP2.rda')
```

# Stratification by maternal nationality
## PTB % by maternal nationality, unadjusted
```{r}
table(bevn_eco_in7$mother_nationality_cat2, bevn_eco_in7$PTB, useNA="always")
round(prop.table(table(bevn_eco_in7$mother_nationality_cat2, bevn_eco_in7$PTB, useNA="always"), margin=1)*100,2)
```

## PTB % stratified by maternal nationality, adjusted for all covariates

```{r include=FALSE}
m_SB_bam_swiss2 <- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_Swiss)
m_SB_bam_Afr2 <- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_Afr)  
m_SB_bam_Asi2 <- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_Asi)  
m_SB_bam_Eur2 <- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_Eur)  
m_SB_bam_Nort_Am2 <- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_Nort_Am)  
m_SB_bam_S_C_Am2 <- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_S_C_Am)  

plot_m_SB_bam_swiss2 <- GAM_plot_function_binary(m_SB_bam_swiss2, 1) %>%
  mutate(nationality="Swiss")
plot_m_SB_bam_Afr2 <- GAM_plot_function_binary(m_SB_bam_Afr2, 1) %>%
  mutate(nationality="African")
plot_m_SB_bam_Asi2 <- GAM_plot_function_binary(m_SB_bam_Asi2, 1) %>%
  mutate(nationality="Asian")
plot_m_SB_bam_Eur2 <- GAM_plot_function_binary(m_SB_bam_Eur2, 1) %>%
  mutate(nationality="European")
plot_m_SB_bam_Nort_Am2 <- GAM_plot_function_binary(m_SB_bam_Nort_Am2, 1) %>%
  mutate(nationality="Northern American")
plot_m_SB_bam_S_C_Am2 <- GAM_plot_function_binary(m_SB_bam_S_C_Am2, 1) %>%
  mutate(nationality="Southern/Central American")
```

```{r}
plot_SB_nationality2 <- plot_m_SB_bam_swiss2 %>%
  rbind(plot_m_SB_bam_Afr2) %>%
  rbind(plot_m_SB_bam_Asi2) %>%
  rbind(plot_m_SB_bam_Eur2) %>%
  rbind(plot_m_SB_bam_Nort_Am2) %>%
  rbind(plot_m_SB_bam_S_C_Am2) %>%
  mutate(x=round(x,0)) %>%
  left_join(x_date) %>%
  mutate(date_x= ymd(paste0(birth_Y_M,"-01")))

ggplot_SB_nationality2 <- ggplot(data=plot_SB_nationality2)+
  geom_line(aes(x=as.POSIXct(date_x),y=fit,col=nationality, linetype=nationality),lwd=lwdline)+
  geom_ribbon(aes(x=as.POSIXct(date_x),ymin=CIl,ymax=CIu,fill=nationality),alpha=0.15,lwd=lwdline)+
  xlab("Timeline (years)")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.001,0.007)) +
  scale_colour_manual('Maternal nationality',
                      limits=c("Swiss","African", "Asian", "European", "Northern American", "Southern/Central American"),
                      values =c("#69D8F3","gold", "#8B0000", "hotpink", "lightgreen", "#666975"))+
  scale_fill_manual('Maternal nationality',
                    limits=c("Swiss","African", "Asian", "European", "Northern American", "Southern/Central American"),
                      values =c("#69D8F3","gold", "#8B0000", "hotpink", "lightgreen", "#666975"))+
  scale_x_datetime( breaks = date_breaks("12 month"), 
                    labels = label_date_short(),
                    limits =c(as.POSIXct("2007-01-01"), max(lim2)),
                    expand = c(0,0)) +
  scale_linetype_manual('Maternal nationality',
                        limits = c("Swiss", "African", "Asian", "European", "Northern American", "Southern/Central American"),
                        values = c("solid", "dashed", "dotted", "dotdash", "longdash", "twodash")) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom",
        legend.key.width = unit(1.5, "cm"), 
        legend.key.height = unit(0.5, "cm"))+
theme(axis.title.x = axis.title.x.position)
ggplot_SB_nationality2
# 
# save(ggplot_PTB_nationality2, file='output/figures_paper/ggplot_PTB_nationality2.rda')
```

# Stratification by langage region
## PTB % by langage region, unadjusted
```{r}
table(bevn_eco_in7$Language, bevn_eco_in7$PTB, useNA="always")
round(prop.table(table(bevn_eco_in7$Language, bevn_eco_in7$PTB, useNA="always"), margin=1)*100,2)
```

## PTB % stratified by langage region, adjusted for all other covariates

```{r include=FALSE}
m_SB_bam_German2<- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_German) 
m_SB_bam_French2<- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_French)  
m_SB_bam_Italian2<- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_Italian)  
 
plot_m_SB_bam_German2 <- GAM_plot_function_binary(m_SB_bam_German2, 1) %>%
  mutate(language_region="German")
plot_m_SB_bam_French2 <- GAM_plot_function_binary(m_SB_bam_French2, 1) %>%
  mutate(language_region="French")
plot_m_SB_bam_Italian2 <- GAM_plot_function_binary(m_SB_bam_Italian2, 1) %>%
  mutate(language_region="Italian")
```

```{r}
plot_SB_language2 <- plot_m_SB_bam_German2 %>%
  rbind(plot_m_SB_bam_French2) %>%
  rbind(plot_m_SB_bam_Italian2) %>%
  mutate(x=round(x,0)) %>%
  left_join(x_date) %>%
  mutate(date_x= ymd(paste0(birth_Y_M,"-01")))

ggplot_SB_Language_region2 <- ggplot(data=plot_SB_language2)+
  geom_line(aes(x=as.POSIXct(date_x),y=fit,col=language_region, linetype=language_region),lwd=lwdline)+
  geom_ribbon(aes(x=as.POSIXct(date_x),ymin=CIl,ymax=CIu,fill=language_region),alpha=0.15,lwd=lwdline)+
  xlab("Timeline (years)")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.001,0.007)) +
  scale_colour_manual('Language region',
                      limits=c("German","French", "Italian"),
                      values =c("aquamarine","cadetblue1", "aquamarine4"))+
  scale_fill_manual('Language region',
                    limits=c("German","French", "Italian"),
                      values =c("aquamarine","cadetblue1", "aquamarine4"))+
  scale_x_datetime( breaks = date_breaks("12 month"), 
                    labels = label_date_short(),
                    limits =c(as.POSIXct("2007-01-01"), max(lim2)),
                    expand = c(0,0)) +
  scale_linetype_manual('Language region',
                        limits = c("German", "French", "Italian"),
                        values = c("solid", "dashed", "dotted")) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom",
        legend.key.width = unit(1.5, "cm"), 
        legend.key.height = unit(0.5, "cm")) +
theme(axis.title.x = axis.title.x.position)
ggplot_SB_Language_region2

#save(ggplot_PTB_Language_region2, file='output/figures_paper/ggplot_PTB_Language_region2.rda')
```

# Stratification by sex
```{r include=FALSE}
m_SB_males <- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_males)  
m_SB_females <- bam(stillbirth ~ s(birth_Y_M_num), family="binomial", data=bevn_eco_in6_females)  

plot_m_SB_males <- GAM_plot_function_binary(m_SB_males, 1) %>%
  mutate(Sex="Males")
plot_m_SB_females <- GAM_plot_function_binary(m_SB_females, 1) %>%
  mutate(Sex="Females")

```

```{r}
plot_data_sex <- plot_m_SB_males %>%
  rbind(plot_m_SB_females) %>%
  mutate(x=round(x,0)) %>%
  left_join(x_date) %>%
  mutate(date_x= ymd(paste0(birth_Y_M,"-01")))

plot_SB_sex <- ggplot(data=plot_data_sex)+
  geom_line(aes(x=as.POSIXct(date_x),y=fit,col=Sex, linetype=Sex),lwd=lwdline)+
  geom_ribbon(aes(x=as.POSIXct(date_x),ymin=CIl,ymax=CIu,fill=Sex),alpha=0.15,lwd=lwdline)+
  xlab("Timeline (years)")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.001, 0.007)) +
  scale_colour_manual('Sex',
                      limits=c("Males","Females"),
                      values =c("magenta","purple"))+
  scale_fill_manual('Sex',
                    limits=c("Males","Females"),
                      values =c("magenta","purple"))+
  scale_x_datetime( breaks = date_breaks("12 month"), 
                    labels = label_date_short(),
                    limits =c(as.POSIXct("2007-01-01"), max(lim2)),
                    expand = c(0,0)) +
  scale_linetype_manual('Sex',
                        limits = c("Males", "Females"),
                        values = c("solid", "dashed")) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom",
        legend.key.width = unit(1.5, "cm"), 
        legend.key.height = unit(0.5, "cm"))  +
        theme(axis.title.x = axis.title.x.position)
plot_SB_sex

tabtest <- bevn_eco_in6 %>%
    group_by(sex,birthyear) %>%
  summarise(n=n(),
    count_SB_1 = sum(stillbirth=="1", na.rm=T), percent_SB_1=100*count_SB_1/n )%>%
    ungroup()
```
