---
title: "Graphics"
author: "Mathilde Le Vu"
date:  "`r Sys.Date()`"
html_document: 
output:
  rmdformats::robobook:
    code_folding: show
    self_contained: true
    highlight: pygments
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Add labels 
```{r}
my_labels <- c(mat_age = "maternal age (years)", 
               parity_cat = "parity",
               civil_status3= "civil status",
               mean_ssep2= "mean SSEP",
               mean_Alt_mean2="mean altitude",
               BW="birth weight (g)", 
               Language="language region",
               Urban3="urbanity",
               mother_nationality_cat2="maternal nationality",
               sex="sex",
               GA_weeks="gestational age (weeks)",
               stillbirth="stillbirth",
               PTB="preterm birth (<37 weeks) ", LBW="low birth weight (<2'500g)"
              )
 bevn_eco_in6_graph <- bevn_eco_in6
 
 label(bevn_eco_in6_graph) <- as.list(my_labels[match(names(bevn_eco_in6_graph), # Assign labels to data frame variables
                             
                                                                     names(my_labels))])
label(bevn_eco_in6_graph)
bevn_eco_in6_graph <- bevn_eco_in6_graph%>%
  mutate(mother_nationality_cat2= case_when(is.na(mother_nationality_cat2) ~ "Missing or Oceanian",
                                             TRUE ~as.character(mother_nationality_cat2)),
         Language=case_when(is.na(Language) ~"Missing",
                            TRUE ~as.character(Language)),
          Urban3=case_when(is.na(Urban3) ~"Missing",
                            TRUE ~as.character(Urban3)),
          parity_cat=case_when(is.na(parity_cat) ~"Missing",
                            TRUE ~as.character(parity_cat)),
         across(c(mother_nationality_cat2, Language, Urban3,parity_cat), as.factor)) 
  

attr(bevn_eco_in6_graph$stillbirth, 'levels')<- c("livebirth", "stillbirth")
attr(bevn_eco_in6_graph$sex, 'levels')<- c("Male", "Female")
attr(bevn_eco_in6_graph$PTB, "levels")<- c('term', 'preterm')
attr(bevn_eco_in6_graph$LBW, "levels")<- c('normal BW', 'LBW')
attr(bevn_eco_in6_graph$parity_cat, "levels")<- c('1', '2', '3', '>3',"Missing")

desired_order_nat <- c("Missing or Oceanian","Northern America","Southern and Central America","Africa","Asia","Europe","Switzerland")  # Replace with your desired order
desired_order_lang <- c("Missing", "Italian","French","German or Romansh")
levels(bevn_eco_in6_graph$Urban3)<- c("Rural","Urban", "Missing")
desired_order_urb<- c("Missing", "Urban","Rural")
desired_order_parity<- c("Missing",">3", "3","2", "1")


bevn_eco_in6_graph <- bevn_eco_in6_graph %>%
  mutate(mother_nationality_cat2 = factor(mother_nationality_cat2, levels = desired_order_nat),
         Language = factor(Language, levels = desired_order_lang),
         Urban3 = factor(Urban3, levels = desired_order_urb),
         parity_cat = factor(parity_cat, levels = desired_order_parity))

bevn_eco_in6_graph$civil_status3 <- relevel(bevn_eco_in6_graph$civil_status3, ref="Single")
bevn_eco_in6_graph$sex <- relevel(bevn_eco_in6_graph$sex, ref="Male")

table(bevn_eco_in6_graph$mother_nationality_cat2)
table(bevn_eco_in6_graph$Urban3)
table(bevn_eco_in6_graph$civil_status3)
table(bevn_eco_in6_graph$parity_cat)
table(bevn_eco_in6_graph$sex)
table(bevn_eco_in6_graph$PTB)
table(bevn_eco_in6_graph$LBW)
table(bevn_eco_in6_graph$stillbirth)

 label(bevn_eco_in6_graph) <- as.list(my_labels[match(names(bevn_eco_in6_graph), # Assign labels to data frame variables
                                            names(my_labels))])
label(bevn_eco_in6_graph)
```

# Categorical variables
## maternal nationality through the years
```{r}
custom_colors <- c("grey","#98F5FF", "#68228B", "#7FFFD4", "#CD8C95", "#FFB6C1","#53868B")  # Replace with your desired colors

gg_nation_birthy <- ggplot(bevn_eco_in6_graph,
       aes(x=birthyear, fill=mother_nationality_cat2)) + 
  geom_bar(position = "fill", stat="count") +
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  scale_x_continuous(breaks = seq(2007,2022, by=2))+
  scale_fill_manual(values=custom_colors)+
  labs(x="",
       y="",
       fill="Maternal nationality")+theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_nation_birthy
```

## maternal civil status through the years
```{r}
custom_colors <- c("#FFB6C1","#53868B") 

gg_civil_status_birthy <- ggplot(bevn_eco_in6_graph,
       aes(x=birthyear, fill=civil_status3)) + 
  geom_bar(position = "fill", stat="count") +
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  scale_x_continuous(breaks = seq(2007,2022, by=2))+
  scale_fill_manual(values=custom_colors)+
  labs(x="",
       y="",
       fill="Maternal civil status") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_civil_status_birthy
```

## language region through the years
```{r}
custom_colors <- c("grey","#7FFFD4","#FFB6C1","#53868B") 

gg_lang_region_birthy <- ggplot(bevn_eco_in6_graph,
       aes(x=birthyear, fill=Language)) + 
  geom_bar(position = "fill", stat="count") +
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  scale_x_continuous(breaks = seq(2007,2022, by=2))+
  scale_fill_manual(values=custom_colors)+
  labs(x="",
       y="",
       fill="Language region")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_lang_region_birthy
```

## urbanity through the years
```{r}
custom_colors <- c("grey","#FFB6C1","#53868B") 

gg_urban_birthy <- ggplot(bevn_eco_in6_graph,
       aes(x=birthyear, fill=Urban3)) + 
  geom_bar(position = "fill", stat="count") +
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  scale_x_continuous(breaks = seq(2007,2022, by=2))+
  scale_fill_manual(values=custom_colors)+
  labs(x="", y="",
       fill="Urbanity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_urban_birthy
```

## parity through the years
```{r}
custom_colors <- c("grey","#458B74","#7FFFD4","#FFB6C1","#53868B") 

gg_parity_birthy <- ggplot(bevn_eco_in6_graph,
       aes(x=birthyear, fill=parity_cat)) + 
  geom_bar(position = "fill", stat="count") +
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  scale_x_continuous(breaks = seq(2007,2022, by=2))+
  scale_fill_manual(values=custom_colors)+
  labs(x="", y="",
       fill="Parity")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_parity_birthy
```

## sex
```{r}
custom_colors <- c("#FFB6C1","#53868B") 

gg_sex_birthy <- ggplot(bevn_eco_in6_graph,
       aes(x=birthyear, fill=sex)) + 
  geom_bar(position = "fill", stat="count") +
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  scale_x_continuous(breaks = seq(2007,2022, by=2))+
  scale_fill_manual(values=custom_colors)+
  labs(x="",y="",
       fill="neonatal sex")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_sex_birthy
```

## stillbirth
```{r}
custom_colors <- c("#53868B") 

gg_stillbirth_birthy <- bevn_eco_in6_graph %>%
  group_by(birthyear) %>%
  summarise(percentage = sum(stillbirth == "stillbirth") / n()) %>%
  ggplot(aes(x = birthyear, y = percentage)) +
  geom_bar(stat = "identity", fill = custom_colors) +
  scale_y_continuous(labels = scales::percent_format(scale = 100), limits=c(0,0.005)) +
  scale_x_continuous(breaks = seq(2007, 2022, by=2)) +  # Customize x-axis breaks and limits
  labs(x = "", y="") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_stillbirth_birthy
```

## PTB
```{r}
gg_PTB_birthy <- bevn_eco_in6_graph %>%
  group_by(birthyear) %>%
  summarise(percentage = sum(PTB == "preterm") / n()) %>%
  ggplot(aes(x = birthyear, y = percentage)) +
  geom_bar(stat = "identity", fill = custom_colors) +
  scale_y_continuous(labels = scales::percent_format(scale = 100), limits=c(0,0.06)) +
  scale_x_continuous(breaks = seq(2007, 2022, by=2)) +  # Customize x-axis breaks and limits
  labs(x = "",y="") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_PTB_birthy
```

## LBW
```{r}
gg_LBW_birthy <- bevn_eco_in6_graph %>%
  group_by(birthyear) %>%
  summarise(percentage = sum(LBW == "LBW") / n()) %>%
  ggplot(aes(x = birthyear, y = percentage)) +
  geom_bar(stat = "identity", fill = custom_colors) +
  scale_y_continuous(labels = scales::percent_format(scale = 100), limits=c(0,0.06)) +
  scale_x_continuous(breaks = seq(2007, 2022, by=2)) +
  labs(x = "",y=""
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_LBW_birthy
```

# Continuous variables
## maternal age  
```{r}
custom_colors <- c("#98F5FF", "#458B74", "#7FFFD4", "#CD8C95", "#FFB6C1","#53868B")  

gg_birthy_mat_age <- ggplot(bevn_eco_in6_graph, aes(x = birthyear, y = mat_age, group = birthyear)) +
  geom_violin(fill = "#7FFFD4") +  
     labs(x = "", y = "maternal age (years)") +
    scale_x_continuous(breaks = seq(2007, 2022, by=2)) + 
  scale_y_continuous(breaks=seq(10,50,by=5), limits=c(10,50))+
     theme(
       panel.background = element_rect(fill = "white"),
     axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_birthy_mat_age

# colors <- c("#98F5FF", "#FFB6C1")
# gg_birthy_mat_age <- ggplot(bevn_eco_in6_graph, aes(x = birthyear, y = mat_age, group = birthyear, fill = factor(birthyear %% 2, labels = colors))) +# Alternate colors based on birthyear
#   geom_boxplot(show.legend=FALSE) +
#   labs(x = "", y = "Maternal age") +
#   scale_x_continuous(breaks = seq(2007, 2022, by = 2)) + 
#   scale_y_continuous(breaks = seq(10, 50, by = 5)) +
#   theme_bw() +
#   theme(
#     panel.background = element_rect(fill = "white")
#   ) +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1.2))
# gg_birthy_mat_age
# ggplot(bevn_eco_in6_graph, aes(x = birthyear, y = mat_age)) +
#   stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", width = 0.2) +
#   stat_summary(fun.data = "mean_cl_normal", geom = "point", size = 3) +
#   labs(x = "", y = "Maternal age") +
#     scale_x_continuous(breaks = seq(2007, 2022, by=2)) +  
#   theme(axis.text.x = element_text(angle = 45, hjust = 1.2))
```

## mean SSEP
```{r}
gg_birthy_SSEP <- ggplot(bevn_eco_in6_graph, aes(x = birthyear, y = mean_ssep2, group = birthyear)) +
  geom_violin(fill = "#7FFFD4") + 
     labs(x = "", y = "mean SSEP") +
    scale_x_continuous(breaks = seq(2007, 2022, by=2)) + 
  scale_y_continuous(breaks=seq(20,90,by=10), limits=c(20,90))+
     theme(
       panel.background = element_rect(fill = "white"),
     axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_birthy_SSEP
```

## mean altitude
```{r}
gg_birthy_alt  <- ggplot(bevn_eco_in6_graph, aes(x = birthyear, y = mean_Alt_mean2, group = birthyear)) +
  geom_violin(fill = "#7FFFD4") +  
     labs(x = "", y = "mean altitude (MASL)") +
    scale_x_continuous(breaks = seq(2007, 2022, by=2)) + 
  scale_y_continuous(breaks=seq(200,1950,by=400), limits=c(200,1950))+
     theme(
       panel.background = element_rect(fill = "white"),
     axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_birthy_alt
```

## birthweight
```{r}
gg_birthy_BW  <- ggplot(bevn_eco_in6_graph, aes(x = birthyear, y = BW, group = birthyear)) +
  geom_violin(fill = "#7FFFD4") + 
     labs(x = "", y = "birth weight (g)") +
    scale_x_continuous(breaks = seq(2007, 2022, by=2)) + 
  scale_y_continuous(breaks=seq(100,7000,by=500), limits=c(100,7000))+
     theme(
       panel.background = element_rect(fill = "white"),
     axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_birthy_BW
```

## gestational age
```{r}
gg_birthy_GA  <- ggplot(bevn_eco_in6_graph, aes(x = birthyear, y = GA_weeks, group = birthyear)) +
  geom_violin(fill = "#7FFFD4") + 
  labs(x = "", y = "gestational age (weeks)") +
    scale_x_continuous(breaks = seq(2007, 2022, by=2)) + 
  scale_y_continuous(breaks=seq(18,46,by=4), limits=c(18,46))+
     theme(
       panel.background = element_rect(fill = "white"),
     axis.text.x = element_text(angle = 45, hjust = 1.2))
gg_birthy_GA
```

# Kernel plots
## Birthweight 

```{r}
BW_sex <- ggplot(bevn_eco_in7, aes(x=BW, colour=sex)) + geom_density()
BW_sex

BW_birthyear_in7 <- ggplot(bevn_eco_in7, aes(x=BW, colour=as.factor(birthyear))) + geom_density()
BW_birthyear_in7
BW_birthyear_in7 + xlim(1500, 5500)
BW_birthyear_in7 + xlim(3000, 3800)


BW_birthyear_in6 <- ggplot(bevn_eco_in6, aes(x=BW, colour=as.factor(birthyear))) + geom_density()
BW_birthyear_in6
BW_birthyear_in6 + xlim(1500, 5500)
BW_birthyear_in6 + xlim(3000, 3800)

BW_birthyear_in <- ggplot(bevn_eco, aes(x=BW, colour=as.factor(birthyear))) + geom_density()
BW_birthyear_in
BW_birthyear_in + xlim(1500, 5500)
BW_birthyear_in + xlim(3000, 3800)

#maternal age
matage_birthyear_in7 <- ggplot(bevn_eco_in7, aes(x=mat_age, colour=as.factor(birthyear))) + geom_density()
matage_birthyear_in7
```


## Gestational age

```{r}
GA_sex <- ggplot(bevn_eco_in7, aes(x=GA_days, colour=sex)) + geom_density()
GA_sex + xlim(240,300)

GA_birthyear_in <- ggplot(bevn_eco_in7, aes(x=GA_days, colour=as.factor(birthyear))) + geom_density()
GA_birthyear_in
GA_birthyear_in + xlim(240, 300)

GA_birthyear_in6 <- ggplot(bevn_eco_in7, aes(x=GA_days, colour=as.factor(birthyear))) + geom_density()
GA_birthyear_in6
GA_birthyear_in6 + xlim(240, 300)

GA_birthyear_in7 <- ggplot(bevn_eco_in7, aes(x=GA_days, colour=as.factor(birthyear))) + geom_density()
GA_birthyear_in7
GA_birthyear_in7 + xlim(240, 300)
```
## BW categorical, through the years 
```{r}
# p1 <- bevn_eco_in7 %>% 
#   ggplot(aes(x = birthyear, fill = BW_cat3)) + 
#   geom_bar(position = "fill") + 
#   ylab("proportion")
# p1
```

