---
title: "Trimester effect: exposure in 1st vs 3rd trim, BW, PTB, stillbirth. Flu crisis instead of GR"
author: "Mathilde Le Vu"
date:  "`r Sys.Date()`"
html_document: 
output:
  rmdformats::robobook:
    code_folding: show
    self_contained: true
    highlight: pygments
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Birthweight (not adjusted for gestational age)
## First trimester exposure to the crises

```{r}
  m_BW_1st_trim_flu <- bam(BW ~ s(mat_age) + birth_Y_M_num+  s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100+ parity_cat + sex + Urban3 + Language + mother_nationality_cat2 + civil_status3 + HW_first_trimester + flu_first_trimester_relativ  + covid_hosp_1st_trim_relativ, data=bevn_eco_in7) 
    summary(m_BW_1st_trim_flu)
    # extracting the plot information
plot_m_BW_3rd_trim_mat_age_flu <- GAM_plot_function_continuous(m_BW_1st_trim_flu, 1) # mat age
plot_m_BW_3rd_trim_month_flu <- GAM_plot_function_continuous(m_BW_1st_trim_flu, 2) #seasonality
```

### Graph maternal age variable X BW (not adj for GA)

```{r}
plot_BW_3rd_trim_mat_age_flu <- ggplot(data=plot_m_BW_3rd_trim_mat_age_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Maternal age (years)")+
  ylab("Birthweight (g)")+
  coord_cartesian(ylim=c(3160,3380)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(0,60,by=5),expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(0,4000,by=50)) +
theme(axis.title.x = axis.title.x.position)
plot_BW_3rd_trim_mat_age_flu
```

### Graph seasonality X birthweight (not adj for GA)

```{r}
plot_BW_3rd_trim_month_flu <- ggplot(data=plot_m_BW_3rd_trim_month_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Month")+
  ylab("Birthweight (g)")+
  coord_cartesian(ylim=c(3160,3380)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(1,12,by=1),expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(0,4000,by=50)) +
theme(axis.title.x = axis.title.x.position)
plot_BW_3rd_trim_month_flu
```

### Table summarizing the birthweight outcome model (not adj for GA)

```{r}
  beta <- coef(m_BW_1st_trim_flu)
  Vb <- vcov(m_BW_1st_trim_flu, unconditional = TRUE)
  se <- sqrt(diag(Vb))
  n <- 1263853 #to check
  d <- (abs(beta)/(sqrt(n)*se))
  my.ci_BW_1st_trim_flu <- data.frame(cbind(beta, lci = beta-1.96*se, uci = beta + 1.96*se, d))
  my.ci_BW_1st_trim_flu <- format(round(my.ci_BW_1st_trim_flu[18:20, c(1:4)], digits=2), nsmall=2)
```

## Last trimester exposure to the crises

```{r}
    m_BW_last_trim_flu <- bam(BW ~ s(mat_age) + birth_Y_M_num+  s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100+ parity_cat + sex + Urban3 + Language + mother_nationality_cat2 + civil_status3 + HW_last_trimester + flu_last_trimester_relativ  + covid_hosp_last_trim_relativ, data=bevn_eco_in7) 
    summary(m_BW_last_trim_flu) 
# extracting the plot information
plot_m_BW_last_trim_mat_age_flu <- GAM_plot_function_continuous(m_BW_last_trim_flu, 1) # mat age
plot_m_BW_last_trim_month_flu <- GAM_plot_function_continuous(m_BW_last_trim_flu, 2) #seasonality
```

### Graph maternal age variable X BW (not adj for GA)

```{r}
plot_BW_last_trim_mat_age_flu <- ggplot(data=plot_m_BW_last_trim_mat_age_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Maternal age (years)")+
  ylab("Birthweight (g)")+
  coord_cartesian(ylim=c(3160,3380)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(0,60,by=5),expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(0,4000,by=50)) +
theme(axis.title.x = axis.title.x.position)
plot_BW_last_trim_mat_age_flu
```


### Graph seasonality X birthweight (not adj for GA)

```{r}
plot_BW_last_trim_month_flu <- ggplot(data=plot_m_BW_last_trim_month_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Month")+
  ylab("Birthweight (g)")+
  coord_cartesian(ylim=c(3160,3380)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(1,12,by=1),expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(0,4000,by=50)) +
theme(axis.title.x = axis.title.x.position)
plot_BW_last_trim_month_flu
```

### Table summarizing the birthweight outcome model (not adj for GA)

```{r}
 beta <- coef(m_BW_last_trim_flu)
  Vb <- vcov(m_BW_last_trim_flu, unconditional = TRUE)
  se <- sqrt(diag(Vb))
  n <- 1263853 #to check
  d <- (abs(beta)/(sqrt(n)*se))
  my.ci_BW_last_trim_flu <- data.frame(cbind(beta, lci = beta-1.96*se, uci = beta + 1.96*se, d))
  my.ci_BW_last_trim_flu <- format(round(my.ci_BW_last_trim_flu[18:20, c(1:4)], digits=2), nsmall=2)
```

# Stillbirth- simple model, without adjusting for GA
## First trimester exposure
```{r}
  m_SB_1st_trim_flu <- bam(stillbirth ~ s(mat_age) + birth_Y_M_num+  s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100+ sex + Urban3 + Language + mother_nationality_cat1 + civil_status3 + HW_first_trimester + flu_first_trimester_relativ  + covid_hosp_1st_trim_relativ, family="binomial", data=bevn_eco_in6) 
    summary(m_SB_1st_trim_flu)

plot_m_SB_1st_trim_mat_age_flu <- GAM_plot_function_binary(m_SB_1st_trim_flu, 1)
plot_m_SB_1st_trim_month_flu <- GAM_plot_function_binary(m_SB_1st_trim_flu, 2)
  concurvity(m_SB_1st_trim_flu, full = TRUE)
```

### Graph maternal age X Stillbirth

```{r}
plot_SB_1st_trim_mat_age_flu <- ggplot(data=plot_m_SB_1st_trim_mat_age_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Maternal age (years)")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.0005,0.008)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom")+
  scale_x_continuous(breaks=seq(0,60,by=5),expand = c(0, 0)) +
theme(axis.title.x = axis.title.x.position)
plot_SB_1st_trim_mat_age_flu
```

### Graph seasonality X Stillbirth

```{r}
plot_SB_1st_trim_month_flu <- ggplot(data=plot_m_SB_1st_trim_month_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Month")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.0005,0.008)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom")+
  scale_x_continuous(breaks=seq(1,12,by=1),expand = c(0, 0)) +
theme(axis.title.x = axis.title.x.position)
plot_SB_1st_trim_month_flu
```


### Table summarizing the stillbirth outcome model

```{r echo=FALSE}
  OR <- exp(coef(m_SB_1st_trim_flu))
  beta <- coef(m_SB_1st_trim_flu)
  Vb <- vcov(m_SB_1st_trim_flu, unconditional = TRUE)
  se <- sqrt(diag(Vb))
  lci <- exp(beta-1.96*se)
  uci <- exp(beta+1.96*se)
  d <- abs(beta)/1.81
  my.ci_SB_1st_trim_flu <- data.frame(cbind(OR, lci, uci, d))
  my.ci_SB_1st_trim_flu <-  format(round(my.ci_SB_1st_trim_flu[11:13, c(1:4)], digits=2), nsmall=2)
```

## Last trimester exposure
```{r}
m_SB_last_trim_flu <- bam(stillbirth ~ s(mat_age) + birth_Y_M_num+  s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100+ sex + Urban3 + Language + mother_nationality_cat1 + civil_status3 + HW_last_trimester + flu_last_trimester_relativ  + covid_hosp_last_trim_relativ, family="binomial", data=bevn_eco_in6) 
    summary(m_SB_last_trim_flu)

plot_m_SB_last_trim_mat_age_flu <- GAM_plot_function_binary(m_SB_last_trim_flu, 1)
plot_m_SB_last_trim_month_flu <- GAM_plot_function_binary(m_SB_last_trim_flu, 2)
  concurvity(m_SB_last_trim_flu, full = TRUE)
```

### Graph maternal age X Stillbirth

```{r}
plot_SB_last_trim_mat_age_flu <- ggplot(data=plot_m_SB_last_trim_mat_age_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Maternal age (years)")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.0005,0.008)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom")+
  scale_x_continuous(breaks=seq(0,60,by=5),expand = c(0, 0)) +
theme(axis.title.x = axis.title.x.position)
plot_SB_1st_trim_mat_age_flu
```

### Graph seasonality X Stillbirth

```{r}
plot_SB_last_trim_month_flu <- ggplot(data=plot_m_SB_last_trim_month_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Month")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.0005,0.008)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom")+
  scale_x_continuous(breaks=seq(1,12,by=1),expand = c(0, 0)) +
theme(axis.title.x = axis.title.x.position)
plot_SB_1st_trim_month_flu
```

### Table summarizing the stillbirth outcome model

```{r echo=FALSE}
  OR <- exp(coef(m_SB_last_trim_flu))
  beta <- coef(m_SB_last_trim_flu)
  Vb <- vcov(m_SB_last_trim_flu, unconditional = TRUE)
  se <- sqrt(diag(Vb))
  lci <- exp(beta-1.96*se)
  uci <- exp(beta+1.96*se)
  d <- abs(beta)/1.81
  my.ci_SB_last_trim_flu <- data.frame(cbind(OR, lci, uci, d))
  my.ci_SB_last_trim_flu <-  format(round(my.ci_SB_last_trim_flu[11:13, c(1:4)], digits=2), nsmall=2)
```

# Preterm birth (without adjusting for birthweight)
## First trimester exposure 
```{r echo=FALSE}
  m_PTB_1st_trim_flu <- bam(PTB ~ s(mat_age) + birth_Y_M_num+  s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100+ parity_cat+ sex + Urban3 + Language + mother_nationality_cat2 + civil_status3 + HW_first_trimester + flu_first_trimester_relativ  + covid_hosp_1st_trim_relativ, family="binomial", data=bevn_eco_in7) 

    # extracting the plot information
plot_m_PTB_1st_trim_mat_age_flu <- GAM_plot_function_binary(m_PTB_1st_trim_flu, 1)
plot_m_PTB_1st_trim_month_flu <- GAM_plot_function_binary(m_PTB_1st_trim_flu, 2)
```

### Graph maternal age X preterm birth

```{r}
plot_PTB_1st_trim_mat_age_flu <- ggplot(data=plot_m_PTB_1st_trim_mat_age_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Maternal age (years)")+
  ylab("Preterm birth probability")+
  theme_bw()+
  coord_cartesian(ylim=c(0.05,0.14)) +
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(0,60,by=5),expand = c(0, 0)) +
  theme(axis.title.x = axis.title.x.position)
plot_PTB_1st_trim_mat_age_flu
```

### Graph seasonality X preterm birth 
```{r}
plot_PTB_1st_trim_seasonality_flu <- ggplot(data=plot_m_PTB_1st_trim_month_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Month")+
  ylab("Preterm birth probability")+
  theme_bw()+
  coord_cartesian(ylim=c(0.05,0.14)) +
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(1,12,by=1),expand = c(0, 0)) +
  theme(axis.title.x = axis.title.x.position)
plot_PTB_1st_trim_seasonality_flu
```

### Table summarizing the preterm birth outcome model

```{r}
  OR <- exp(coef(m_PTB_1st_trim_flu))
  beta <- coef(m_PTB_1st_trim_flu)
  Vb <- vcov(m_PTB_1st_trim_flu, unconditional = TRUE)
  se <- sqrt(diag(Vb))
  lci <- exp(beta-1.96*se)
  uci <- exp(beta+1.96*se)
  d <- abs(beta)/1.81
  my.ci_PTB_1st_trim_flu <- data.frame(cbind(OR, lci, uci, d))
  my.ci_PTB_1st_trim_flu <- format(round(my.ci_PTB_1st_trim_flu[18:20, c(1:4)], digits=2), nsmall=2)
```


## Last trimester exposure 
```{r echo=FALSE}
  m_PTB_last_trim_flu <- bam(PTB ~ s(mat_age) + birth_Y_M_num+  s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100+ parity_cat+ sex + Urban3 + Language + mother_nationality_cat2 + civil_status3 + HW_last_trimester + flu_last_trimester_relativ  + covid_hosp_last_trim_relativ, family="binomial", data=bevn_eco_in7) 

    # extracting the plot information
plot_m_PTB_last_trim_mat_age_flu <- GAM_plot_function_binary(m_PTB_last_trim_flu, 1)
plot_m_PTB_last_trim_month_flu <- GAM_plot_function_binary(m_PTB_last_trim_flu, 2)
```

### Graph maternal age X preterm birth

```{r}
plot_PTB_last_trim_mat_age_flu <- ggplot(data=plot_m_PTB_last_trim_mat_age_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Maternal age (years)")+
  ylab("Preterm birth probability")+
  theme_bw()+
  coord_cartesian(ylim=c(0.05,0.14)) +
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(0,60,by=5),expand = c(0, 0)) +
  theme(axis.title.x = axis.title.x.position)
plot_PTB_1st_trim_mat_age_flu
```

### Graph seasonality X preterm birth 
```{r}
plot_PTB_last_trim_seasonality_flu <- ggplot(data=plot_m_PTB_last_trim_month_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Month")+
  ylab("Preterm birth probability")+
  theme_bw()+
  coord_cartesian(ylim=c(0.05,0.14)) +
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(1,12,by=1),expand = c(0, 0)) +
  theme(axis.title.x = axis.title.x.position)
plot_PTB_1st_trim_seasonality_flu
```

### Table summarizing the preterm birth outcome model

```{r}
  OR <- exp(coef(m_PTB_last_trim_flu))
  beta <- coef(m_PTB_last_trim_flu)
  Vb <- vcov(m_PTB_last_trim_flu, unconditional = TRUE)
  se <- sqrt(diag(Vb))
  lci <- exp(beta-1.96*se)
  uci <- exp(beta+1.96*se)
  d <- abs(beta)/1.81
  my.ci_PTB_last_trim_flu <- data.frame(cbind(OR, lci, uci, d))
  my.ci_PTB_last_trim_flu <- format(round(my.ci_PTB_last_trim_flu[18:20, c(1:4)], digits=2), nsmall=2)
```


