---
title: "Variables checking"
author: "Mathilde Le Vu"
date: '2022-05-11'
output: html_document
---

```{r setup, include=FALSE}
.libPaths(c("H:/Documents/R/win-library/4.1","C:/Program Files/R/R-4.1.2/library"))
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(dplyr)
```

# Opening the data file
```{r }
bevn <- read.csv2(here("data", "birth_iem.csv"))

```
# Checking each variable has the correct format and content

## Statistikjahr und Ereignisjahr = statistical year and year of birth

Expected Ereignisjahr: from 1987 to 2020, no missing
```{r}
summary(bevn$Statistikjahr)
table(bevn$Statistikjahr, useNA="always")
round(prop.table(table(bevn$Statistikjahr, useNA="always"))*100,2)
summary(bevn$Ereignisjahr)
table(bevn$Ereignisjahr, useNA="always")
round(prop.table(table(bevn$Ereignisjahr, useNA="always"))*100,2)
```

##  Ereignismonat = month of birth

Expected: 1-12
```{r}
summary(bevn$Ereignismonat)
table(bevn$Ereignismonat, useNA="always")
round(prop.table(table(bevn$Ereignismonat, useNA="always"))*100,2)
```
<br>

## Mutter und Vater: Alter in erfüllten Jahren: Age mother/father (fullfilled years)

expected? 10-65 for women and 10-90+ for men?
```{r}
summary(bevn$Mutter..Alter.in.erfüllten.Jahren)
summary(bevn$Vater..Alter.in.erfüllten.Jahren)
```
<br>

## Kind: Geschlecht = sex of the neonate <br>

1=male, 2=female 
```{r}
table(bevn$Kind..Geschlecht, useNA="always")
round(prop.table(table(bevn$Kind..Geschlecht, useNA="always"))*100,2)
```

## Kind: Gestationsalter = gestational age 

in Tagen days, missing=empty, only since 2006 <br>
Expected: 100-308?<br>
Checking that its available since 2006
```{r}
summary(bevn$Kind..Gestationsalter.in.Tagen)

##GA in weeks
bevn$Kind..Gestationsalter.in.Tagen <- as.numeric(bevn$Kind..Gestationsalter.in.Tagen)
bevn$GA_weeks <- bevn$Kind..Gestationsalter.in.Tagen / 7
summary(bevn$GA_weeks)

tapply(bevn$GA_weeks, bevn$Ereignisjahr, summary) 

#calculating mean by year
 group_mean <- aggregate(GA_weeks ~ Ereignisjahr, data = bevn, mean) # Equivalent works
 group_mean

```
Available in 2003 and 2004 as well<br>
Much less NAs from 2007 <br>
From 2006, GA mean is very stable (around 39.15)

## Geburtsort = place of birth (hospital or at home)

Only available until 1997 (ca. 98% in hospitals) <br>
Coding <br>
 1- im Spital	à l’hôpital			1969-1997 <br>
 2- zu Hause	à la maison	1969-1997 <br> 
 3- anderer Ort	autre lieu	1987-1997 <br>
 4- Ort unbekannt	lieu inconnu	1987-1997 <br>
 9- Angabe fehlt	pas d’indication		1987-1997 <br> 

```{r}
table(bevn$Geburtsort, useNA = "always")
round(prop.table(table(bevn$Geburtsort, useNA="always"))*100,2)
round(prop.table(table(bevn$Ereignisjahr, bevn$Geburtsort, useNA = "always"))*100,2)
```
Only available until 1997: okay

## Geburtsstaat = State and world region of birth

See separate codebook <br>
Expected: 8100-8703 <br>
```{r}
#checking min and max values (should be 8100 and 8703)
  summary(bevn$Geburtsstaat)
#8999 doesnt correspond to anything in the codebook but probably NA
  table(bevn$Geburtsstaat, useNA = "always")
#assign NA to values=8999
  bevn$Geburtsstaat[bevn$Geburtsstaat ==8999] = NA
 
# categorizing state of birth in : Switzerland or Outside of Switzerland
  bevn$Geburtsstaat_cat1 <- cut(bevn$Geburtsstaat, breaks=c(8000, 8100, 10000), include.lowest=TRUE, labels=c("Switzerland", "Outside Switzerland"))
  table(bevn$Geburtsstaat_cat1, useNA = "always")
  round(prop.table(table(bevn$Geburtsstaat_cat1, useNA="always"))*100,2)

#categorizing state of birth in : Switzerland, Europe, Africa, Americas, Asia, Oceania, other
  bevn$Geburtsstaat_cat2 <- cut(bevn$Geburtsstaat, breaks=c(8000, 8100, 8280, 8384, 8486, 8601, 8685, 10000), include.lowest=TRUE, labels=c("Switzerland", "Europe - excl Switz", "Africa", "Americas", "Asia", "Oceania", "Other"))
table(bevn$Geburtsstaat_cat2, useNA = "always")
round(prop.table(table(bevn$Geburtsstaat_cat2, useNA="always"))*100,2)

#categorizing state of birth in : Switzerland, different parts of Europe, other
bevn$Geburtsstaat_cat3 <- as.factor(ifelse(bevn$Geburtsstaat == 8100, 'Switz',
                                    ifelse(bevn$Geburtsstaat == 8207 | bevn$Geburtsstaat == 8208 | bevn$Geburtsstaat == 8209 | bevn$Geburtsstaat == 8222 | bevn$Geburtsstaat == 8229 | bevn$Geburtsstaat == 8230 | bevn$Geburtsstaat == 8238 | bevn$Geburtsstaat == 8243 | bevn$Geburtsstaat == 8244,  'Central Europe',
                                    ifelse (bevn$Geburtsstaat == 8201 | bevn$Geburtsstaat == 8205 | bevn$Geburtsstaat ==8220 | bevn$Geburtsstaat == 8232 | bevn$Geburtsstaat == 82880 | (bevn$Geburtsstaat > 8247 & bevn$Geburtsstaat< 8258) , 'SE Europe',
                                    ifelse(bevn$Geburtsstaat==8202 | bevn$Geburtsstaat== 8213 | bevn$Geburtsstaat==8231 |bevn$Geburtsstaat== 8236, 'SW Europe', 
                                    ifelse(bevn$Geburtsstaat==8204 | bevn$Geburtsstaat==8212 |bevn$Geburtsstaat==8215|bevn$Geburtsstaat==8216|bevn$Geburtsstaat==8223|bevn$Geburtsstaat==8225|bevn$Geburtsstaat==8226|bevn$Geburtsstaat==8227|bevn$Geburtsstaat==8270|bevn$Geburtsstaat==8271|bevn$Geburtsstaat==8272|bevn$Geburtsstaat==8275, 'Western Europe',
                                 ifelse(bevn$Geburtsstaat==8206|bevn$Geburtsstaat==8210|bevn$Geburtsstaat==8211|bevn$Geburtsstaat==8217|bevn$Geburtsstaat==8228|bevn$Geburtsstaat==8234|bevn$Geburtsstaat==8273|bevn$Geburtsstaat==8274,'Northern Europe', 
                                ifelse(bevn$Geburtsstaat==8214|bevn$Geburtsstaat==8218|bevn$Geburtsstaat==8224|bevn$Geburtsstaat==8233|bevn$Geburtsstaat==8239|bevn$Geburtsstaat==8241|bevn$Geburtsstaat==8242, 'Southern Europe',
                                ifelse(bevn$Geburtsstaat==8235|bevn$Geburtsstaat==8572|bevn$Geburtsstaat==8573|bevn$Geburtsstaat==8574|bevn$Geburtsstaat==8576|bevn$Geburtsstaat==8577|bevn$Geburtsstaat==8578 | (bevn$Geburtsstaat > 8259 & bevn$Geburtsstaat < 8267), 'Eastern Europe','other')))))))))

round(prop.table(table(bevn$Geburtsstaat_cat3, useNA="always"))*100,2)
```
4 attritbuted to 8999: doesnt correspond to any country in the codebook -> attributed to NA  <br>
95% of total births took place in Switzerland.

## Art der Geburt = number of babies 

1=singleton, 2=twins, 3=triplets, ..., 6=sextuplets and more <br>
Expected: 1-6
```{r}
table(bevn$Art.der.Geburt, useNA="always")
round(prop.table(table(bevn$Art.der.Geburt, useNA="always"))*100,2)
```

## Anzahl Knaben and Anzahl Mädchen =	if multiple birth, number of boys and girls

Expected: 0-5 
```{r}
table(bevn$Anzahl.Knaben, useNA = "always")
table(bevn$Anzahl.Mädchen, useNA = "always")
```

## 11. Kind: Grösse in Zentimeter = length at birth (cm), missing=99

Expected: 10-60? And 99 for missing
```{r}
summary(bevn$Kind..Grösse.in.Zentimeter)
#assign birthlength=99 to NA
bevn$Kind..Grösse.in.Zentimeter[bevn$Kind..Grösse.in.Zentimeter ==99] = NA
summary(bevn$Kind..Grösse.in.Zentimeter)
table(bevn$Kind..Grösse.in.Zentimeter, useNA = "always")
round(prop.table(table(bevn$Kind..Grösse.in.Zentimeter, useNA="always"))*100,2)
```
Many are set to 0 (missing? should have been set to 99). Outliers (1-10?)
4.33% are NAs
--> we should choose a threshold for inclusion in the db.

## Kind: Gewicht in Gramm = weight at birth (g), missing=9999 

Expected: 10-6000 and 9999
```{r}
summary(bevn$Kind..Gewicht.in.Gramm)
#assign BW=9999 or BW=0 to NA
bevn$Kind..Gewicht.in.Gramm[bevn$Kind..Gewicht.in.Gramm ==9999 |bevn$Kind..Gewicht.in.Gramm==0] = NA
summary(bevn$Kind..Gewicht.in.Gramm)
HBW <- subset(bevn, Kind..Gewicht.in.Gramm>6000) #having a look at high birthweight neonates : 1 extreme outlier at 9351g
table(HBW$Kind..Gewicht.in.Gramm)
VLBW <- subset(bevn, Kind..Gewicht.in.Gramm<100) #having a look at (extreme) low birthweight neonates : many are set to 0, many are also below 100
table(VLBW$Kind..Gewicht.in.Gramm)
```

outliers (BW=9.3kg, or BW <<<100...)<br>
 
## Kind: Rang in der aktuellen Ehe

Expected: 1-15
```{r}
table(bevn$Kind..Rang.in.der.aktuellen.Ehe, useNA="always")
round(prop.table(table(bevn$Kind..Rang.in.der.aktuellen.Ehe, useNA="always"))*100,2)
```

## Mutter: Staatsangehörigkeit = Nationality Mother, see separate codebook 

Expected: 8100-8703
```{r}
summary(bevn$Mutter..Staatsangehörigkeit)
table(bevn$Mutter..Staatsangehörigkeit, useNA="always")

# categorizing nationality of the mother in : Switzerland or Outside of Switzerland
  bevn$mother_nationality_cat1 <- cut(bevn$Mutter..Staatsangehörigkeit, breaks=c(8000, 8100, 10000), include.lowest=TRUE, labels=c("Switzerland", "Outside Switzerland"))
  round(prop.table(table(bevn$mother_nationality_cat1, useNA="always"))*100,2)
  
# categorizing state of birth in : Switzerland, Europe, Africa, Americas, Asia, Oceania, other
  bevn$mother_nationality_cat2 <- cut(bevn$Mutter..Staatsangehörigkeit, breaks=c(8000, 8100, 8280, 8384, 8486, 8601, 8685, 10000), include.lowest=TRUE, labels=c("Switzerland", "Europe - excl Switz", "Africa", "Americas", "Asia", "Oceania", "Other"))
round(prop.table(table(bevn$mother_nationality_cat2, useNA="always"))*100,2)
```
8998, 8999?  NAs?  <br>

## Mutter Zivilstand = additional variable  

See additional codebook <br>
 1 - Single	from 1969 <br>
 2- Married	from 1969 <br>
 3- Widowed	from 1969 <br>
 4- Divorced	from 1969 <br>
 5- Unmarried	from 1998 <br>
 6- Registered partnership from 2007 <br>
 7- Partnership dissolved	from 2007 <br>
```{r}
round(prop.table(table(bevn$Mutter.Zivilstand, useNA="always"))*100,2)
table(bevn$Mutter.Zivilstand, bevn$Ereignisjahr, useNA="always")
```
categories 1, 2, 3 are available in all years (ok) <br>
category 5 available since 1998 (ok) <br>
categroy 6 available since 2006 (1 year earlier) <br>
category 7 available since 2066 (1 year earlier) <br>
 
 
## Mutter: Wohngemeinde / Wohnstaat =  Place of residence Mother

GMDNR or country, see separate codebook <br>
Expected: <br>
1-6910 for commune if resident inside Switz <br>
8201-8703 if resident outside of Switz <br>
```{r}
#to check minimum and maximum
summary(bevn$Mutter..Wohngemeinde...Wohnstaat)
#assign Mutter..Wohngemeinde...Wohnstaat=8999 to NA
bevn$Mutter..Wohngemeinde...Wohnstaat[bevn$Mutter..Wohngemeinde...Wohnstaat ==8999] = NA
# categorizing place of residence of the mother in : inside or outside Switzerland
  bevn$mother_residence_cat1 <- cut(bevn$Mutter..Wohngemeinde...Wohnstaat, breaks=c(0, 6911, 8704), include.lowest=TRUE, labels=c("Switzerland", "Outside Switzerland"))
  round(prop.table(table(bevn$mother_residence_cat1, useNA="always"))*100,2)
  table(bevn$mother_residence_cat1, useNA="always")
```

## Empty variables
- Mutter: Stellung im Beruf (NA) <br>
- Mutter: Beruf (NA) <br>
- Vater/Ernährer: Stellung im Beruf (NA) <br>
- Vater/Ernährer: Beruf (NA) <br>
```{r}
summary(bevn$Mutter..Stellung.im.Beruf)
summary(bevn$Mutter..Beruf)
summary(bevn$Vater.Ernährer..Stellung.im.Beruf)
table(bevn$Vater.Ernährer..Stellung.im.Beruf, useNA="always")
summary(bevn$Vater.Ernährer..Beruf)
```
Vater.Ernährer..Stellung.im.Beruf is not empty: shouldnt it be? <br>
Coding Vater.Ernährer..Stellung.im.Beruf:  <br>
1		indépendant  <br>
2		collaborateur familial  <br>
3		directeur/-trice, fondé(e) de pouvoir, fonctionnaire  ayant une fonction de chef  <br>
4		autre  <br>
9		inconnu  <br>
<br>

## Vater: Staatsangehörigkeit = Nationality father, see separate codebook

Expected: 8100-8703
```{r}
#checking min and max
summary(bevn$Vater..Staatsangehörigkeit)
#assign Vater..Staatsangehörigkeit=8999 to NA
bevn$Vater..Staatsangehörigkeit[bevn$Vater..Staatsangehörigkeit ==8999|bevn$Vater..Staatsangehörigkeit ==8998] = NA
# categorizing nationality of the father in : inside or outside Switzerland
  bevn$father_nationality_cat1 <- cut(bevn$Vater..Staatsangehörigkeit, breaks=c(8000, 8100, 8704), include.lowest=TRUE, labels=c("Switzerland", "Outside Switzerland"))
  round(prop.table(table(bevn$father_nationality_cat1, useNA="always"))*100,2)
  table(bevn$father_nationality_cat1, useNA="always")
```
Same remark than for the mother: 8998, 899? NAs? to check <br>

## Kind: biologischer Rang
```{r}
table(bevn$Kind..biologischer.Rang, useNA = "always")
round(prop.table(table(bevn$Kind..biologischer.Rang, useNA="always"))*100,2)
```
Many missing biological rank, but we also have the variable Kind.rang.in.der.aktuelle.ehe.

## Flag variables: what is their use?
```{r}
summary(bevn$Flag..Geschlecht.des.Kindes)
table(bevn$Flag..Geschlecht.des.Kindes, useNA = "always")
summary(bevn$Flag..Art.der.Geburt)
table(bevn$Flag..Art.der.Geburt, useNA = "always")
summary(bevn$Flag..Rang.des.Kindes.in.der.aktuellen.Ehe)
table(bevn$Flag..Rang.des.Kindes.in.der.aktuellen.Ehe, useNA = "always")
summary(bevn$Flag..Zivilstand.der.Mutter)
table(bevn$Flag..Zivilstand.der.Mutter, useNA = "always")
```
Apart form Flag..Zivilstand.der.Mutter, the other variables make no sense --> probably not useful

## Mutter: ständig oder nicht-ständiger Wohnsitz = Residence of the mother

Coding <br>
1=permanent resident, 2=non-permanent resident, 4=short stay, 9=domiciled abroad
```{r}
summary(bevn$Mutter..ständig.oder.nicht.ständiger.Wohnsitz)
table(bevn$Mutter..ständig.oder.nicht.ständiger.Wohnsitz, useNA = "always")
round(prop.table(table(bevn$Mutter..ständig.oder.nicht.ständiger.Wohnsitz, useNA="always"))*100,2)
```

## Vater und Mutter: Alter in erreichten Jahren = Age father and mother (approximated)
```{r}
summary(bevn$Vater..Alter.in.erreichten.Jahren)
table(bevn$Vater..Alter.in.erreichten.Jahren, useNA = "always")
summary(bevn$Mutter..Alter.in.erreichten.Jahren)
table(bevn$Mutter..Alter.in.erreichten.Jahren, useNA = "always")
```

##  lebend geboren oder nicht = born alive or not

1=lifeborn, 2=stillborn
```{r}
table(bevn$lebend.geboren.oder.nicht, useNA = "always")
round(prop.table(table(bevn$lebend.geboren.oder.nicht, useNA="always"))*100,3)
 stillborn <- subset(bevn, lebend.geboren.oder.nicht==2)
 round(prop.table(table(stillborn$Ereignisjahr))*100,2)
#calculating median GA by year of birth, for stillborn
 GA_median <- aggregate(GA_weeks ~ Ereignisjahr, data = stillborn, median) 
 GA_median
#GA was only systematically recorded from 2006 
 #calculating median BW for stillborn babies, by year
  BW_median <- aggregate(Kind..Gewicht.in.Gramm ~ Ereignisjahr, data = stillborn, median) 
  BW_median
```
GA seems stable across years for stillbron: 28-31weeks
but stillborn BW seems to vary accross years (730-2135g)


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
