---
title: "Descriptive and univariate analysis"
author: "Mathilde Le Vu"
date:  "`r Sys.Date()`"
html_document: 
output:
  rmdformats::robobook:
    code_folding: show
    self_contained: true
    highlight: pygments
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Characteristics of the population
(variable by variable)

## Year and month of birth
```{r}
#month of birth
round(prop.table(table(bevn_eco$month))*100,2)
round(prop.table(table(bevn_eco_in7$month))*100,2)
#year of birth
round(prop.table(table(bevn_eco$birthyear))*100,2)
round(prop.table(table(bevn_eco_in7$birthyear))*100,2)
```


## State and world region of birth

```{r}
# State of birth in : Switzerland or Outside of Switzerland
  table(bevn_eco$country_of_birth_cat1, useNA = "always")
  round(prop.table(table(bevn_eco$country_of_birth_cat1, useNA="always"))*100,2)

#State of birth in : Switzerland, Europe, Africa, Americas, Asia, Oceania, other
  table(bevn_eco$country_of_birth_cat2, useNA = "always")
  round(prop.table(table(bevn_eco$country_of_birth_cat2, useNA="always"))*100,2)

#State of birth in : Switzerland, different parts of Europe, other
  round(prop.table(table(bevn_eco$country_of_birth_cat3, useNA="always"))*100,2)
```

There are **124,074** births that occurred outside of Switzerland.

## Nationality Mother

```{r}
summary(bevn_eco$mother_nationality)

# Nationality of the mother in : Switzerland or Outside of Switzerland
  round(prop.table(table(bevn_eco$mother_nationality_cat1, useNA="always"))*100,2)
  round(prop.table(table(bevn_eco_in7$mother_nationality_cat1, useNA="always"))*100,2)
  round(prop.table(table(bevn_eco_in6$mother_nationality_cat1, useNA="always"))*100,2)

# Nationality of the mother in : Switzerland, Europe, Africa, Northern America, Southern America, Asia, Oceania, other
  round(prop.table(table(bevn_eco$mother_nationality_cat2, useNA="always"))*100,2)
  round(prop.table(table(bevn_eco_in7$mother_nationality_cat2, useNA="always"))*100,2)
  round(prop.table(table(bevn_eco_in6$mother_nationality_cat2, useNA="always"))*100,2)
  table(bevn_eco_in6$mother_nationality_cat2, useNA="always")
#Nationality of the mother in : Switzerland, different parts of Europe, other
  round(prop.table(table(bevn_eco$mother_nationality_cat3, useNA="always"))*100,2)
  round(prop.table(table(bevn_eco_in7$mother_nationality_cat3, useNA="always"))*100,2)
```

## Place of residence Mother

1-6910 for commune if resident inside Switz <br> 8201-8703 if resident outside of Switz <br>

```{r}
#to check minimum and maximum
summary(bevn_eco$com)
head(bevn_eco$com,50)

# Place of residence of the mother in : inside or outside Switzerland
  round(prop.table(table(bevn_eco$mother_residence_cat1, useNA="always"))*100,2)
  table(bevn_eco$mother_residence_cat1, useNA="always")

```

## Status of Residence of the mother

1=permanent resident, 2=non-permanent resident, 4=short stay, 9=domiciled abroad

```{r}
summary(bevn_eco$resident_status)
table(bevn_eco$resident_status, useNA = "always")
round(prop.table(table(bevn_eco$resident_status, useNA="always"))*100,2)

table(bevn_eco$mother_nationality_cat1, bevn_eco$resident_status)
```
There are **158,606** women domiciled abroad

## Nationality father

See separate codebook. Expected: 8100-8703

```{r}
# categorizing nationality of the father in : inside or outside Switzerland
  round(prop.table(table(bevn_eco$father_nationality_cat1, useNA="always"))*100,2)
  table(bevn_eco$father_nationality_cat1, useNA="always")
  round(prop.table(table(bevn_eco_in7$father_nationality_cat1, useNA="always"))*100,2)
  table(bevn_eco_in7$father_nationality_cat1, useNA="always")
```

## Born alive or not

1=lifeborn, 2=stillborn

```{r}
table(bevn_eco$stillbirth, useNA = "always")
round(prop.table(table(bevn_eco$stillbirth, useNA="always"))*100,3)
round(prop.table(table(bevn_eco_in6$stillbirth, useNA="always"))*100,3)
```

## Sex
```{r}
table(bevn_eco$sex, useNA = "always")
round(prop.table(table(bevn_eco$sex, useNA="always"))*100,3)
table(bevn_eco_in6$sex, useNA = "always")
round(prop.table(table(bevn_eco_in6$sex, useNA="always"))*100,3)
table(bevn_eco_in7$sex, useNA = "always")
round(prop.table(table(bevn_eco_in7$sex, useNA="always"))*100,3)
```

## Gestational age

```{r}
## GA in weeks
summary(bevn_eco$GA_weeks)
summary(bevn_eco_in6$GA_weeks)
summary(bevn_eco_in7$GA_weeks)
##PTB
summary(bevn_eco$PTB)
round(prop.table(table(bevn_eco$PTB, useNA="always"))*100, 3)
summary(bevn_eco_in6$PTB)
round(prop.table(table(bevn_eco_in6$PTB, useNA="always"))*100, 3)
summary(bevn_eco_in7$PTB)
round(prop.table(table(bevn_eco_in7$PTB, useNA="always"))*100, 3)
```

## Length at birth (cm)


```{r}
summary(bevn_eco$BL)
table(bevn_eco$BL, useNA = "always")
summary(bevn_eco_in6$BL)
summary(bevn_eco_in7$BL)
```

## Weight at birth (g)


```{r}
summary(bevn_eco$BW)
summary(bevn_eco_in7$BW)

#BW categ. in LBW (<2500g) or not (>2500)
table(bevn_eco$LBW, useNA="always")
round(prop.table(table(bevn_eco$LBW, useNA="always"))*100, 3)
table(bevn_eco_in7$LBW, useNA="always")
round(prop.table(table(bevn_eco_in7$LBW, useNA="always"))*100, 3)

table(bevn_eco$Bw_Macro, useNA="always")
round(prop.table(table(bevn_eco$Bw_Macro, useNA="always"))*100, 3)
table(bevn_eco_in7$Bw_Macro, useNA="always")
round(prop.table(table(bevn_eco_in7$Bw_Macro, useNA="always"))*100, 3)
```

There are **124,331** births with missing BW.


## Number of babies 

1=singleton, 2=twins, 3=triplets, ..., 6=sextuplets and more <br>
```{r}
table(bevn_eco$nb_of_babies, useNA="always")
round(prop.table(table(bevn_eco$nb_of_babies, useNA="always"))*100,2)
##Single VS multiple pregnancies
table(bevn_eco$singleton_or_multiple)
round(prop.table(table(bevn_eco$singleton_or_multiple, useNA="always"))*100,2)
```

There are **48,139** multiple births in the original dataset.

## Parity
```{r}
table(bevn_eco$parity_cat, useNA = "always")
round(prop.table(table(bevn_eco$parity_cat, useNA="always"))*100,2)
table(bevn_eco_in7$parity_cat, useNA = "always")
round(prop.table(table(bevn_eco_in7$parity_cat, useNA="always"))*100,2)
```

## Maternal and paternal age
```{r}
summary(bevn_eco$mat_age)
summary(bevn_eco_in7$mat_age)
round(prop.table(table(bevn_eco_in7$mat_age_cat))*100,2)

summary(bevn_eco$pat_age)
summary(bevn_eco_in7$pat_age)
 table(bevn_eco_in7$pat_age_cat, useNA = "always")
 round(prop.table(table(bevn_eco_in7$pat_age_cat))*100,2)
```

## Age difference between parents
```{r}
summary(bevn_eco_in7$parent_age_diff)
```


# Ecological variables 

## Language
```{r}
  table(bevn_eco$Language,  useNA="always")
  round(prop.table(table(bevn_eco$Language,  useNA="always"))*100,2)
  table(bevn_eco_in7$Language,  useNA="always")
  round(prop.table(table(bevn_eco_in7$Language,  useNA="always"))*100,2)
```

## Urban variables
1 is urban, 0 is rural

```{r}
 table(bevn_eco$Urban3)
 round(prop.table(table(bevn_eco$Urban3,  useNA="always"))*100,2)
round(prop.table(table(bevn_eco_in7$Urban3,  useNA="always"))*100,2)
```


## Grossregion

```{r}
table(bevn_eco$Grossregion)
round(prop.table(table(bevn_eco$Grossregion,  useNA="always"))*100,2)
round(prop.table(table(bevn_eco_in7$Grossregion,  useNA="always"))*100,2)
```

## Altitude

```{r}
summary(bevn_eco$mean_Alt_mean2)
summary(bevn_eco_in7$mean_Alt_mean2)
summary(bevn_eco_in6$mean_Alt_mean2)
```

## SSEP

```{r}
summary(bevn_eco$mean_ssep2)
summary(bevn_eco_in7$mean_ssep2)
summary(bevn_eco_in6$mean_ssep2)
```



# Simple tables: variables through the year

## Gestational age through the years
```{r}
#calculating median by year
 GA_median <- aggregate(GA_weeks ~ birthyear, data = bevn_eco_in7, median) # from 2006 it was systematically collected
 GA_median

#same but using tidyverse
 gamedian <- bevn_eco_in7 %>%
   group_by(birthyear) %>%
     filter( !is.na(GA_weeks)) %>%
   summarise(medGA=format(median(GA_weeks),digits=5))
ungroup(gamedian)


# Calculate the GA mode through the years
ga_mode <- bevn_eco_in7 %>%
   group_by(birthyear) %>%
     filter( !is.na(GA_weeks)) %>%
   summarise(mode=format(getmode(GA_weeks), digits=7))
ungroup(ga_mode)

## GA frequency tables through the years
boxplot(GA_weeks ~birthyear, data=bevn_eco_in7)
  #subset with GA over 35 weeks
  boxplot(GA_weeks ~birthyear, data=bevn_eco_in7, subset = GA_weeks>35)
```

## Mother nationality through the years

```{r}
gg_nation_birthy <- ggplot(bevn_eco_in7,
       aes(x=birthyear, fill=mother_nationality_cat2)) + 
  geom_bar(position = "fill") 

gg_nation_birthy +  ggtitle("Maternal nationality through the years") +
 scale_x_continuous(breaks = c(2007, 2010, 2013, 2016, 2020))
```


## Birthweight through time

```{r}
#birthweight through the years
BW_median2 <- aggregate(BW ~ birthyear, data = bevn_eco_in7, median) 
BW_median2
boxplot(BW~birthyear, data=bevn_eco_in7, subset= BW<8000)

#birthweight by month
boxplot(BW~month, data=bevn_eco_in7, subset= BW<8000)
```

Birthweight median barely varies between 2007 and 2020, 3340-3360g.

## Birth length through the years

```{r}
BL_median <- aggregate(BL ~ birthyear, data = bevn_eco_in7, median) 
BL_median
boxplot(BL~birthyear, data=bevn_eco_in7)
```

Birthlength median is robustly consistent at 50cm, 2007-2020.

## Sex % through the years

```{r}
table(bevn_eco_in7$sex, bevn_eco_in7$birthyear)
round(prop.table(table(bevn_eco_in7$sex, bevn_eco_in7$birthyear), margin=2)*100,2)
```

Sex ratio is rather stable through the years.

## Stillbirth % through the years, their median/mode GA and BW

### Gestational age of stillborn babies
```{r}
table(bevn_eco_in6$stillbirth, bevn_eco_in6$birthyear, useNA="always")
round(prop.table(table(bevn_eco_in6$stillbirth, bevn_eco_in6$birthyear), margin=2)*100,3)

#calculating median GA by year of birth, for stillborn, with tidyverse
  GA_SB_Y <- bevn_eco_in6 %>%
  group_by(birthyear) %>%
  filter(stillbirth==1) %>% 
   filter(!is.na(GA_weeks)) %>% 
    summarise(medGA=format(median(GA_weeks),digits=5))   
  ungroup(GA_SB_Y) 

#calculating mode GA by year of birth, for stillborn
  ga_y_mode <- bevn_eco_in6 %>%
   group_by(birthyear) %>%
     filter( !is.na(GA_weeks)) %>%
     filter(stillbirth==1) %>% 
   summarise(mode=format(getmode(GA_weeks), digits=5))
  ungroup(ga_y_mode)

#GA categrory for stillbirths
 GA_SB <- bevn_eco_in6 %>%
     filter(stillbirth==1) 
  table(GA_SB$GA_weeks_cat)
  round(prop.table(table(GA_SB$GA_weeks_cat))*100,2)
  
#GA frequency for stillbirths, through the years
  boxplot(GA_weeks~birthyear, data=GA_SB)
```

Median GA for stillbirths varies between 31.143 (2017) and 34.357 (2016) weeks between 2007 and 2020.

### Birthweight of stillborn babies
```{r}
 #calculating median BW for stillborn babies, by year
  BW_median_sb <- aggregate(BW ~ birthyear, data = subset(bevn_eco_in6, stillbirth==1), median) 
  BW_median_sb
  
 #calculating mode BW for stillborn babies, by year
  BW_y_mode <- bevn_eco_in6 %>%
   group_by(birthyear) %>%
     filter( !is.na(BW)) %>%
     filter(stillbirth==1) %>% 
   summarise(mode=format(getmode(BW), digits=5))
  ungroup(BW_y_mode)

  #Low BW frequency for stillbirths, through the years
  BW_SB_Y_freq <- bevn_eco_in6 %>%
   group_by(birthyear) %>%
  filter(stillbirth==1) %>% 
   filter(!is.na(BW)) 
  
 round(prop.table(table(BW_SB_Y_freq$LBW,BW_SB_Y_freq$birthyear), margin=2)*100,2)
 boxplot(BW~birthyear, data=bevn_eco_in6, subset=BW<8000)
```

Median BW for stillbirths varies a lot through the years, between 1500g and 2070g.

## Maternal age through the years

```{r}
AM_median <- aggregate(mat_age ~ birthyear, data = bevn_eco_in7, median)
AM_median

boxplot(mat_age~birthyear, data=bevn_eco_in7)
```

Maternal age increases from 31 to 32 yo between 2006 and 2020.


## Age difference between parents, through the years
```{r}
summary(bevn_eco_in7$parent_age_diff)
agediff_y <- aggregate(parent_age_diff ~ birthyear, data = bevn_eco_in7, median)
agediff_y
```


## Time variables

I created two variables for date : one combining month+year only (birth_Y_M), and another combining day+month+year (birth_Y_M_1stday).
I set up day to 1st of each month in order to have variable m-d-y, easier to work with.

```{r}
  #month year
  tail(bevn_eco_in7$birth_Y_M)
  head(bevn_eco_in7$birth_Y_M)

  #day month year
  summary(bevn_eco_in7$birth_Y_M_1stday)
  tail(bevn_eco_in7$birth_Y_M_1stday)
  head(bevn_eco_in7$birth_Y_M_1stday)
```


# Simple plots

## BW or BL depending on GA

```{r}
#BW and GA, all birthweights
plot(bevn_eco$GA_weeks,bevn_eco$BW) 
#BL and GA, all birthlengths
plot(bevn_eco$GA_weeks, bevn_eco$BL) 
#BW and BL, all
plot(bevn_eco$BW, bevn_eco$BL) 

```

```{r}
#with data set bevn_eco_in7
plot(bevn_eco_in7$GA_weeks, bevn_eco_in7$BW) 
plot(bevn_eco_in7$GA_weeks, bevn_eco_in7$BL)
plot(bevn_eco_in7$BW,bevn_eco_in7$BL)
```


# UNIVARIATE ANALYSIS

## BIRTHWEIGHT

### Birthweight change through the years: Simple model

```{r BW through time}
m_BW_years <- lm(BW~birthyear, data=bevn_eco_in7)
summary(m_BW_years)

#change by day+month+year
m_BW_time2_num <- lm(BW~birth_Y_M_1stday_num, data=bevn_eco_in7)
summary(m_BW_time2_num)

#change by month+year
m_BW_time3_num <- lm(BW~birth_Y_M_num, data=bevn_eco_in7)
summary(m_BW_time3_num)
m_BW_time4_num <- lm(BW~birthmonth, data=bevn_eco_in7)
summary(m_BW_time4_num)

#change by month: seasonal
m_BW_month <- lm(BW~month1, data=bevn_eco_in7)
summary(m_BW_month)
```

### BW related to sex
```{r}
m_BW_sex <- lm(BW~sex, data=bevn_eco_in7)
summary(m_BW_sex) #male is the reference (male=1, female=2)
```

### BW related to maternal age or to parity
```{r BW related to mat age/parity}
m_BW_mat_age <- lm(BW~mat_age, data=bevn_eco_in7)
summary(m_BW_mat_age)

m_BW_mat_age_cat <- lm(BW~mat_age_cat, data=bevn_eco_in7)
summary(m_BW_mat_age_cat)

m_BW_parity <- lm(BW~parity, data=bevn_eco_in7)
summary(m_BW_parity)

m_BW_parity_cat <- lm(BW~parity_cat, data=bevn_eco_in7)
summary(m_BW_parity_cat)
```

### BW related to mother nationality
```{r}
m_BW_nat_cat1 <- lm(BW ~mother_nationality_cat1, data=bevn_eco_in7)
summary(m_BW_nat_cat1)
m_BW_nat_cat2 <- lm(BW ~mother_nationality_cat2, data=bevn_eco_in7)
summary(m_BW_nat_cat2)
```

### BW related to GA
```{r}
m_BW_GA <- lm(BW ~GA_weeks, data=bevn_eco_in7)
summary(m_BW_GA)
m_BW_PTB <- lm(BW~PTB, data=bevn_eco_in7)
summary(m_BW_PTB)
```

### BW category and language region
```{r}
  table(bevn_eco$LBW, bevn_eco$Language)
  round(prop.table(table(bevn_eco$LBW,bevn_eco$Language, useNA="always"), margin=2)*100,2)
  table(bevn_eco_in7$LBW, bevn_eco_in7$Language)
  round(prop.table(table(bevn_eco_in7$LBW,bevn_eco_in7$Language, useNA="always"), margin=2)*100,2)
  m_Bw_lang <- lm(BW~Language, data=bevn_eco_in7)
  summary(m_Bw_lang)
```

### BW related to Urbanicity
```{r}
m_BW_urban <- lm(BW ~Urban3, data=bevn_eco_in7)
summary(m_BW_urban)
```

### BW related to ssep
```{r}
m_BW_ssep <- lm(BW ~mean_ssep2, data=bevn_eco_in7)
summary(m_BW_ssep)
```
- Time (2007-2020): Birthweight slighlty evolved through time: +0.27g/year, equivalent to +0.022g/month, which is not relevant. 
Seasonal effect: compared to babies born in January, babies born in May are a bit heavier (+4.9g) and those born in december are a bit lighter (-10g), but this doesnt seem very relevant, with 12 different month categories. Only a smoothed model can help us aknowledge the possible non-linear effect of month.

- Sex: Males are around 132.05g heavier than females.

- BW is not impacted by maternal age as a continuous variable, but it is impacted by maternal age as a categorical variable (with age category 25-30 as ref): 
 Babies are much lighter for matage 11-20 and 41-70 (-85 and -51g, respectively).
 Babies are a little bit lighter for mat age 21-25 and 36-40 (-9.9 and -2.0g, respectively)
- BW is rather impacted by parity: higher parities are associated with higher BW (71.8g/parity). Compared to primiparous women, when parity=2 there is an increase of +121g. For 3rd parities, BW is increased by 158g. Over 3rd parities, BW increases by 171g.

- BW increases with GA : each GA longer by a week is associated with an increase of 177g. Babies born preterm are about 1kg lighter than those born at term.

- Mother nationality: compared to Swiss mothers, babies born from non-Swiss mothers are heavier by 16g. 
Babies born from African, European, Northern American or Oceanian women are respectively 17.1g, 24.5g, 50.1g, 60.1g heavier than babies born from Swiss mothers. Babies born from Asian or South/Centr American mothers are respectively 49.2g and 7.5g lighter.

- Language region: babies born in French- or Italian-speaking Switzerland are lighter than those born in German/Romansh speaking Switzerland, respectively -63.9g and -94.8g.

- Urbanicity: no impact on BW.

- SSEP: each 1 point increase in SSEP results in a 1g increase in BW.

## STILLBIRTH

Stillbirth related to sex, time, seasonal monthly effect, maternal age, parity, GA, BW, maternal nationality, socio-eco variables (Urbanicity, language region, ssep)

```{r}
#sex
  m_SB_sex <- glm(stillbirth~sex, 
                    family= "binomial",data=bevn_eco_in6)
  summary(m_SB_sex) 

#date of birth
  m_SB_birthyear <- glm(stillbirth~birthyear, 
                    family= "binomial",data=bevn_eco_in6)
  summary(m_SB_birthyear) 

  m_SB_birthday <- glm(stillbirth~birth_Y_M_1stday_num, 
                    family= "binomial",data=bevn_eco_in6)
  summary(m_SB_birthday) 

  m_SB_birthmonth <- glm(stillbirth~birth_Y_M_num, 
                    family= "binomial",data=bevn_eco_in6)
  summary(m_SB_birthmonth) 

  m_month_seasonal <- glm(stillbirth~month1, family = "binomial", data=bevn_eco_in6)
  summary(m_month_seasonal)

#maternal age
  #continuous
  m_SB_mat_age <- glm(stillbirth~mat_age, 
                    family= "binomial",data=bevn_eco_in6)
  summary(m_SB_mat_age) 
  exp(coef(summary(m_SB_mat_age)))[,"Estimate"]
  exp(confint(m_SB_mat_age))  
  #categorical
  m_SB_mat_age_cat <- glm(stillbirth~mat_age_cat, 
                    family= "binomial",data=bevn_eco_in6)
  summary(m_SB_mat_age_cat) 
  exp(coef(summary(m_SB_mat_age_cat)))[,"Estimate"]
  exp(confint(m_SB_mat_age_cat))  

#parity
  m_SB_parity <- glm(stillbirth~parity, 
                    family= "binomial",data=bevn_eco_in6)
  summary(m_SB_parity) 

  m_SB_parity_cat <- glm(stillbirth~parity_cat, 
                    family= "binomial",data=bevn_eco_in6)
  summary(m_SB_parity_cat) 

#gestational age
  m_SB_GA <- glm(stillbirth ~GA_weeks, family="binomial", data=bevn_eco_in6)
  summary(m_SB_GA) 
  exp(coef(summary(m_SB_GA)))[,"Estimate"]
  exp(confint(m_SB_GA))  
 #PTB
  m_SB_PTB <- glm(stillbirth ~PTB, family="binomial", data=bevn_eco_in6)
  summary(m_SB_PTB) 
  exp(coef(summary(m_SB_PTB)))[,"Estimate"]
  exp(confint(m_SB_PTB))  
  
#birthweight
  # BW cat in <2500g, 2500-4000, and >400g
  m_SB_BW_cat3 <- glm(stillbirth ~BW_cat3, family="binomial", data=bevn_eco_in6)
  summary(m_SB_BW_cat3)
  exp(coef(summary(m_SB_BW_cat3)))[,"Estimate"]
  exp(confint(m_SB_BW_cat3))    
  #LBW
  m_SB_LBW <- glm(stillbirth ~LBW, family="binomial", data=bevn_eco_in6)
  summary(m_SB_LBW)
  exp(coef(summary(m_SB_LBW)))[,"Estimate"]
  exp(confint(m_SB_LBW))  
  
#maternal nationality
  m_SB_nat_cat1 <- glm(stillbirth ~mother_nationality_cat1, family="binomial", data=bevn_eco_in6)
  summary(m_SB_nat_cat1) 
  exp(coef(summary(m_SB_nat_cat1)))[,"Estimate"]
  exp(confint(m_SB_nat_cat1)) 
  
  m_SB_nat_cat2 <- glm(stillbirth ~mother_nationality_cat2, family="binomial", data=bevn_eco_in6)
  summary(m_SB_nat_cat2) 
  exp(coef(summary(m_SB_nat_cat2)))[,"Estimate"]
  exp(confint(m_SB_nat_cat2)) 

#Urbanicity
  m_SB_Urban <- glm(stillbirth ~Urban3, family="binomial", data=bevn_eco_in6)
  summary(m_SB_Urban) 

#Language region
  table(bevn_eco$stillbirth, bevn_eco$Language)
  round(prop.table(table(bevn_eco$stillbirth,bevn_eco$Language, useNA="always"), margin=2)*100,2)
  table(bevn_eco_in6$stillbirth, bevn_eco_in6$Language)
  round(prop.table(table(bevn_eco_in6$stillbirth,bevn_eco_in6$Language, useNA="always"), margin=2)*100,2)

  m_SB_lang <- glm(stillbirth~Language, family="binomial", data=bevn_eco_in6)
  summary(m_SB_lang)
  exp(coef(summary(m_SB_lang)))[,"Estimate"]
  exp(confint(m_SB_lang)) 

#SSEP
   ssep2median <- bevn_eco_in6 %>%
   group_by(stillbirth) %>%
     filter( !is.na(mean_ssep2)) %>%
   summarise(medssep2=format(median(mean_ssep2),digits=5))
  ungroup(ssep2median)

  boxplot(mean_ssep2 ~stillbirth, data=bevn_eco_in6)
 
  m_SB_ssep <- glm(stillbirth~mean_ssep2, family="binomial", data=bevn_eco_in6)
  summary(m_SB_ssep)
  exp(coef(summary(m_SB_ssep)))[,"Estimate"]
  exp(confint(m_SB_ssep))
```

Date of birth (monthly seasonal, year of birth, or time (month X year), sex of the baby, parity, urbanicity, have no impact on SB risk.

Increasing maternal age by one year is significantly associated with an increase of SB risk (pvalue: 0.0013), but this increase is very small. 
Maternal age category is also associated with changes in SB risk: being in age categories 11-20, 21-25, 36-40 or 41-70 increases the risk of having a stillborn (compared to age category 25-30). The risk is the greatest for mothers aged 41-70.

Gestational age impacts greatly the risk of stillbirth: with each increasing GA week, the risk is divided by 1.5 (OR=0.65). Being born preterm (<37weeks) multiplies by 40 the risk of stillbirth.

BW category impacts of course SB risk: being born low birthweight (BW<2.5kg) multiplies by 45 the risk of being stillborn, compared to a "normal" BW of 2500-4000g. Belonging to the macrosoma BW category (>4kg), the risk of being stillborn is devided by 1.7 (OR=0.6).

Nationality: being born from a non-Swiss mother multiplies by 1.14 the risk of stillbirth, compared to being born from a Swiss mother. The risk is the highest for mothers with an African origin (OR 1.75) and Europe (1.10).

Language: being born in French speaking Switzerland multiples by 1.23 the risk of being stillborn, compared to being born in German-speaking Switzerland. There is no risk associated with stillbirth in Italian-speaking Switzerland area.

Increasing SSEP slightly reduces stillbirth risk (OR=.99)