---
title: "GAM all variables different outcomes, crises: pooling trimesters. Without adj. for GA in"
author: "Mathilde Le Vu"
date:  "`r Sys.Date()`"
html_document: 
output:
  rmdformats::robobook:
    code_folding: show
    self_contained: true
    highlight: pygments
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Birthweight (not adjusted for gestational age)

```{r}
m_BW3 <- bam(BW ~ s(mat_age) + s(birth_Y_M_num, k=7)+  s(month, bs="cc") + s(mean_ssep2) + s(mean_Alt_mean2)+ parity_cat + sex + Urban3 + Language + mother_nationality_cat2 + civil_status3 + HW + GR_relativ_total + covid_hosp_relativ_total, data=bevn_eco_in7) 
summary(m_BW3)
 m_BW_covid <- bam(BW ~ s(mat_age) + birth_Y_M_num+  s(month, bs="cc") + mean_ssep2 + mean_Alt_mean2 + parity_cat + sex + Urban3 + Language + mother_nationality_cat2  + covid_hosp_relativ_total, data=bevn_eco_in7) 
 m_BW_GR<- bam(BW ~ s(mat_age) + birth_Y_M_num+  s(month, bs="cc") + mean_ssep2 + mean_Alt_mean2 + parity_cat + sex + Urban3 + Language + mother_nationality_cat2  + GR_relativ_total, data=bevn_eco_in7) 
 m_BW_HW <- bam(BW ~ s(mat_age) + birth_Y_M_num+  s(month, bs="cc") + mean_ssep2 + mean_Alt_mean2 + parity_cat + sex + Urban3 + Language + mother_nationality_cat2  + HW, data=bevn_eco_in7) 

 # m_BW3test <- bam(BW ~ s(mat_age) + birth_Y_M_num+  s(month, bs="cc") + mean_ssep2 + mean_Alt_mean2 + parity_cat + sex + Urban3 + Language + mother_nationality_cat2  + HW + GR_relativ_total + covid_hosp_relativ_total, data=bevn_eco_in7) 
 m_BW3 <- bam(BW ~ s(mat_age) + birth_Y_M_num+  s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100 + parity_cat + sex + Urban3 + Language + mother_nationality_cat2  +civil_status3+ HW + GR_relativ_by_pregn_month + covid_hosp_relativ_by_pregn_month, data=bevn_eco_in7)
  summary(m_BW3)

  k.check(m_BW3)
cor(bevn_eco_in7$birth_Y_M_num, bevn_eco_in7$GR_relativ_by_pregn_month)

# extracting the plot information
plot_m_BW_main_mat_age <- GAM_plot_function_continuous(m_BW3, 1) # mat age
# plot_m_BW_main_time <- GAM_plot_function_continuous(m_BW3, 2) # time
plot_m_BW_main_month <- GAM_plot_function_continuous(m_BW3, 2) #seasonality
# plot_m_BW_main_ssep <- GAM_plot_function_continuous(m_BW3, 4) # ssep
# plot_m_BW_main_altitude <- GAM_plot_function_continuous(m_BW3, 5) # altitude
```

## Graph maternal age variable X BW (not adj for GA)

```{r}
plot_BW_main_mat_age <- ggplot(data=plot_m_BW_main_mat_age)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Maternal age (years)")+
  ylab("Birthweight (g)")+
  coord_cartesian(ylim=c(3160,3380)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(0,60,by=5),expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(0,4000,by=50)) +
theme(axis.title.x = axis.title.x.position)
plot_BW_main_mat_age
```


## Graph time X birthweight

```{r}
x_date <-   bevn_eco_in7 %>% #careful, mayhave to change the dataset if I later work with smaller time ranges!
  select(birth_Y_M, birth_Y_M_num) %>%
  distinct(birth_Y_M, .keep_all = TRUE) %>%
  rename(x=birth_Y_M_num)

plot_data_BW <- plot_m_BW_main_time %>%
  mutate(x=round(x,0)) %>%
  left_join(x_date) %>%
  mutate(date_x= ymd(paste0(birth_Y_M,"-01")))

lim1 <- as.POSIXct(ymd("2007-01-01"))
lim2 <- as.POSIXct(ymd("2021-12-01"))

plot_BW_time <- ggplot(data=plot_data_BW)+
  geom_line(aes(x=as.POSIXct(date_x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=as.POSIXct(date_x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Timeline (years)")+
  ylab("Birthweight (g)")+
  coord_cartesian(ylim=c(3250,3550)) +
  scale_colour_manual('BW',  #colour manual is for the line
                      # labels=c("fully adjusted","95% CI","95% CI"),
                      values =c("#9557DC"))+
  scale_fill_manual('BW',                        # fill is for CI
                    # labels=c("fully adjusted","95% CI","95% CI"),
                    values =c("#9557DC"))+
   scale_x_datetime( breaks = date_breaks("12 month"),
                    labels = label_date_short(),
                    limits =c(as.POSIXct("2007-01-01"), max(lim2)), #to force labelling from 2007 on the x axis
                    expand = c(0,0)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom",
         legend.key.width = unit(1.5, "cm"),
        legend.key.height = unit(0.5, "cm")) +
theme(axis.title.x = axis.title.x.position)
plot_BW_time
```

## Graph seasonality X birthweight (not adj for GA)

```{r}
plot_BW_main_month <- ggplot(data=plot_m_BW_main_month)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Month")+
  ylab("Birthweight (g)")+
  coord_cartesian(ylim=c(3160,3380)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(1,12,by=1),expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(0,4000,by=50)) +
theme(axis.title.x = axis.title.x.position)
plot_BW_main_month
```

## Graph SSEP X birthweight (not adj for GA)

```{r}
plot_BW_main_ssep <- ggplot(data=plot_m_BW_main_ssep)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("SSEP")+
  ylab("Birthweight (g)")+
  coord_cartesian(ylim=c(3160,3380)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(0,100,by=5),expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(0,4000,by=50)) +
theme(axis.title.x = axis.title.x.position)
plot_BW_main_ssep
```

## Graph altitude X birthweight (not adj for GA)

```{r}
plot_BW_main_altitude <- ggplot(data=plot_m_BW_main_altitude)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Altitude (MASL)")+
  ylab("Birthweight (g)")+
  coord_cartesian(ylim=c(3160,3380)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(0,2000,by=200),expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(0,4000,by=50)) +
theme(axis.title.x = axis.title.x.position)
plot_BW_main_altitude
```

## Table summarizing the birthweight outcome model (not adj for GA)

```{r}
  beta <- coef(m_BW3)
  Vb <- vcov(m_BW3, unconditional = TRUE)
  se <- sqrt(diag(Vb))
  n <- 1263853 #to check
  d <- (abs(beta)/(sqrt(n)*se))
  my.ci <- data.frame(cbind(beta, lci = beta-1.96*se, uci = beta + 1.96*se, d))
 tab_BW_bam <- round(head(my.ci,20), 2)
```

```{r}
tab_BW_bam['Variable'] <- c("Intercept", 
                            "Time (by month)", "SSEP (/10 points)",
                            "Altitude (/100m)",
                            "Parity (ref: 1)", " ", " ", 
                              "Sex (ref: male)", "Urban (ref: rural)",
                              "Language region (ref: German)", " ", 
                              "Maternal nationality (ref: Swiss)", " ", " ",
                              " ", " ",
                              "Civil status (ref: married)",
                              "Heatwave (ref: 0)",
                            "Great Recession (continuous)",
                              "COVID (continuous)")

    tab_BW_bam['Category'] <- c(" ", 
                                " "," "," ",
                                "2", "3", ">3", "Female", "Urban", "French", "Italian", 
                            "Africa", "Asia", "Europe", "Northern America",
                            "Southern/Central America", "Single", "1", "","")
    tab_BW_bam<-tab_BW_bam[, c('Variable', "Category", "beta", "lci","uci", "d")]

    
tab_BW_bam_gt <- tab_BW_bam %>%
  gt()%>%
  tab_header(title=md(gt::html("**Table 4.A : Association between birthweight and <br> neonatal, maternal and ecological factors from a GAM (model 1.1)**")),
               subtitle = "linear and categorical variables") %>%
  tab_spanner(label = "95% CI (g)", columns = c(lci, uci)) %>%
  tab_style(
    style = list(
          cell_fill(color = "#E0E0E0")
        ),
        locations = cells_body(rows=c(2, 4, 8, 10,11,
                                      17,19)))%>%
    tab_style(
    style = list(
     cell_fill(color = "#F2F0F0")),
        locations = cells_body(rows=c(3, 5, 6, 7, 9, 12, 13,
                                      14,15,16,18,20))) %>%
   tab_options(table.width = pct(35), data_row.padding = px(1),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14,
              source_notes.font.size = 12) %>%
  tab_source_note(source_note = "n=1,263,853")
tab_BW_bam_gt

BW_estimates_main_gt <- tab_BW_bam_gt %>%
  gtsave(here("output/tables_paper", "BW_estimates_main_gt.html"))
BW_estimates_main_gt <- tab_BW_bam_gt %>%
  gtsave(here("output/tables_paper", "BW_estimates_main_gt.docx"))
```


## Table summarizing smooth term pvalues of the BW model (not adj for GA)
```{r}
 pvalues_smooth_BW_main = summary(m_BW3)
 pvalues_smooth_BW_main <- pvalues_smooth_BW_main$s.table[,4]
  pvalues_smooth_BW_main <- format(pvalues_smooth_BW_main, scientific=FALSE)

  pvalues_smooth_BW_main_df <- data.frame(pvalues_smooth_BW_main) %>%
  dplyr::mutate(Variable=c("Maternal age", "Seasonality")) %>%
    rename(c(pvalue=(pvalues_smooth_BW_main)))%>%
    mutate(pvalue=as.numeric(pvalue)) %>%
    mutate(pvalue1=pvalue) 
  
  pvalues_smooth_BW_main_df$pvalue <-  format(round(pvalues_smooth_BW_main_df$pvalue, digits=3), nsmall=2)
  
  pvalues_smooth_BW_main_df <- pvalues_smooth_BW_main_df %>%
    mutate(pvalue1=case_when((pvalue1<0.00001) ~ "<0.0001",
                             (pvalue1<0.001)~ "<0.001")) 
  
  pvalues_smooth_BW_main_df$pvalue1 <- (ifelse(is.na(pvalues_smooth_BW_main_df$pvalue1), pvalues_smooth_BW_main_df$pvalue,                                                 pvalues_smooth_BW_main_df$pvalue1))
  
  pvalues_smooth_BW_main_gt <- pvalues_smooth_BW_main_df %>%
    select(-one_of('pvalue')) %>%
    rename("p-value"="pvalue1") %>%
    gt()%>% 
    tab_header(title=md(gt::html("**Table 4.B : Birthweight GAM (model 1.1)**")), 
              subtitle = "smooth variables") %>%
  tab_options(table.width = pct(10), data_row.padding = px(1),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14,
              source_notes.font.size = 12) 
  pvalues_smooth_BW_main_gt

  BW_main_smooth_pvalues_gt <- pvalues_smooth_BW_main_gt%>%
  gtsave(here("output/tables_paper", "pvalues_smooth_BW_main_gt.html"))
  BW_main_smooth_pvalues_gt <- pvalues_smooth_BW_main_gt%>%
    gtsave(here("output/tables_paper", "pvalues_smooth_BW_main_gt.docx"))
```



# Stillbirth- simple model, without adjusting for GA

```{r}
m_SB_no_crises <- bam(stillbirth~ s(mat_age) + birth_Y_M_num+ s(month, bs="cc") + mean_ssep2 + mean_Alt_mean2 + sex + Urban3 + Language + mother_nationality_cat1 + civil_status3, family="binomial", data=bevn_eco_in6)

# m_SB_crises <- bam(stillbirth~ s(mat_age) + birth_Y_M_num+ s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100 + sex + Urban3 + Language + mother_nationality_cat1 + civil_status3 + HW + GR_relativ_total + covid_hosp_relativ_total, family="binomial", data=bevn_eco_in6)
#   k.check(m_SB_crises) 
#   summary(m_SB_crises)

   m_SB_crises_covid <- bam(stillbirth ~s(mat_age) + birth_Y_M_num + s(month, bs="cc") + mean_ssep2 + mean_Alt_mean2 + sex +Urban3 + Language + mother_nationality_cat1 +civil_status3 + covid_hosp_relativ_total, family="binomial", data=bevn_eco_in6)  
   summary(m_SB_crises_covid) 

      m_SB_crises_GR <- bam(stillbirth ~s(mat_age) + birth_Y_M_num + s(month, bs="cc") + mean_ssep2 + mean_Alt_mean2 + sex +Urban3 + Language + mother_nationality_cat1 +civil_status3 + GR_relativ_total, family="binomial", data=bevn_eco_in6) 
 summary(m_SB_crises_GR) 
 
 m_SB_crises_HW <- bam(stillbirth ~s(mat_age) + birth_Y_M_num + s(month, bs="cc") + mean_ssep2 + mean_Alt_mean2 + sex +Urban3 + Language + mother_nationality_cat1 +civil_status3 + HW, family="binomial", data=bevn_eco_in6)
  summary(m_SB_crises_HW) 
  
  m_SB_crises <- bam(stillbirth~ s(mat_age) + birth_Y_M_num+ s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100 + sex + Urban3 + Language + mother_nationality_cat1 + civil_status3 + HW + GR_relativ_by_pregn_month + covid_hosp_relativ_by_pregn_month, family="binomial", data=bevn_eco_in6)

  
plot_m_SB_main_mat_age <- GAM_plot_function_binary(m_SB_crises, 1)
# plot_m_SB_main_time <- GAM_plot_function_binary(m_SB_crises, 1)
plot_m_SB_main_month <- GAM_plot_function_binary(m_SB_crises, 2)
# plot_m_SB_main_SSEP <- GAM_plot_function_binary(m_SB_crises, 4)
# plot_m_SB_main_alt <- GAM_plot_function_binary(m_SB_crises, 5)

concurvity(m_SB_main, full = TRUE)
```

## Graph maternal age X Stillbirth

```{r}
plot_SB_main_mat_age <- ggplot(data=plot_m_SB_main_mat_age)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Maternal age (years)")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.0005,0.01)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom")+
  scale_x_continuous(breaks=seq(0,60,by=5),expand = c(0, 0)) +
theme(axis.title.x = axis.title.x.position)
plot_SB_main_mat_age
```

## Graph time X Stillbirth

```{r}
x_date <-   bevn_eco_in6 %>% #careful, mayhave to change the dataset if I later work with smaller time ranges!
  select(birth_Y_M, birth_Y_M_num) %>%
  distinct(birth_Y_M, .keep_all = TRUE) %>%
  rename(x=birth_Y_M_num)

plot_data_SB <- plot_m_SB_main_time %>%
  mutate(x=round(x,0)) %>%
  left_join(x_date) %>%
  mutate(date_x= ymd(paste0(birth_Y_M,"-01")))

plot_SB_time <- ggplot(data=plot_data_SB)+
  geom_line(aes(x=as.POSIXct(date_x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=as.POSIXct(date_x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Timeline (years)")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.0005,0.008)) +
   scale_x_datetime( breaks = date_breaks("12 month"), 
                    labels = label_date_short(),
                    limits =c(as.POSIXct("2007-01-01"), max(lim2)),
                    expand = c(0,0)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
theme(axis.title.x = axis.title.x.position)
plot_SB_time
```

## Graph seasonality X Stillbirth

```{r}
plot_SB_main_month <- ggplot(data=plot_m_SB_main_month)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Month")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.0005,0.01)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom")+
  scale_x_continuous(breaks=seq(1,12,by=1),expand = c(0, 0)) +
theme(axis.title.x = axis.title.x.position)
plot_SB_main_month
```

## Graph SSEP X Stillbirth

```{r}
plot_SB_main_SSEP <- ggplot(data=plot_m_SB_main_SSEP)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("SSEP")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.0005,0.008)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom")+
  scale_x_continuous(breaks=seq(0,100,by=5),expand = c(0, 0)) +
theme(axis.title.x = axis.title.x.position)
plot_SB_main_SSEP
```

## Graph altitude X Stillbirth

```{r}
plot_SB_main_altitude <- ggplot(data=plot_m_SB_main_alt)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Altitude (MASL)")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.0005,0.008)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom")+
  scale_x_continuous(breaks=seq(0,2000,by=200),expand = c(0, 0)) +
theme(axis.title.x = axis.title.x.position)
plot_SB_main_altitude
```

## Table summarizing the stillbirth outcome model

```{r echo=FALSE}
  OR <- exp(coef(m_SB_crises))
  beta <- coef(m_SB_crises)
  Vb <- vcov(m_SB_crises , unconditional = TRUE)
  se <- sqrt(diag(Vb))
  lci <- exp(beta-1.96*se)
  uci <- exp(beta+1.96*se)
  d <- abs(beta)/1.81
  my.ci <- data.frame(cbind(OR, lci, uci, d))
  tab_SB_main <-  round(head(my.ci, 13), 2)
```

```{r}
tab_SB_main['Variable'] <- c("Intercept", 
                             "Time (by month)","SSEP (/10 points)",
                            "Altitude (/100m)",
                             "Sex (ref: male)", "Urban (ref: rural)",
 "Language region (ref: German)", " ", 
  "Maternal nationality (ref: Swiss)", 
 "Civil status (ref: married)",
   "Heatwave (ref: 0)", "Great Recession (continuous)","COVID (continuous)")

    tab_SB_main['Category'] <- c(" ", 
                                 " "," "," ",
                                 "Female", "Urban", "French", "Italian", "Not Swiss", "Single", "1", "","")
    tab_SB_main<-tab_SB_main[, c('Variable', "Category", "OR", "lci","uci", "d")]

SB_main_gt <- tab_SB_main %>%
  gt()%>%
  tab_header(title=md(gt::html("**Table 6.A : Association between the risk of stillbirth and <br> neonatal, maternal and ecological factors from a GAM (model 3.1)**")),
            subtitle = "linear and categorical variables") %>%
  tab_spanner(label = "95% CI", columns = c(lci, uci)) %>%
  tab_style(
    style = list(
          cell_fill(color = "#E0E0E0")
        ),
        locations = cells_body(rows=c(2, 4, 6, 9, 11, 13)))%>%
    tab_style(
    style = list(
     cell_fill(color = "#F2F0F0")),
        locations = cells_body(rows=c(3, 5, 7, 8, 10,12))) %>%
  tab_options(table.width = pct(35), data_row.padding = px(1),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14,
              source_notes.font.size = 12) %>%
  tab_source_note(source_note = "n=1,270,114")
SB_main_gt

SB_estimates_main_gt <- SB_main_gt%>%
  gtsave(here("output/tables_paper", "SB_estimates_main_gt.html"))
SB_estimates_main_gt <- SB_main_gt%>%
  gtsave(here("output/tables_paper", "SB_estimates_main_gt.docx"))
```


## Table summarizing smooth term pvalues of the stillbirth model

```{r}
  pvalues_smooth_SB_main = summary(m_SB_crises)
  pvalues_smooth_SB_main <- pvalues_smooth_SB_main$s.table[,4]
  pvalues_smooth_SB_main <- format(pvalues_smooth_SB_main, scientific=FALSE)

  pvalues_smooth_SB_main_df <- data.frame(pvalues_smooth_SB_main) %>%
  dplyr::mutate(Variable=c("Maternal age", "Seasonality")) %>%
  rename(c(pvalue=(pvalues_smooth_SB_main)))%>%
  mutate(pvalue=as.numeric(pvalue)) %>%
  mutate(pvalue1=pvalue) 
  
  pvalues_smooth_SB_main_df$pvalue <-  format(round(pvalues_smooth_SB_main_df$pvalue, digits=3), nsmall=2)

  pvalues_smooth_SB_main_df <- pvalues_smooth_SB_main_df %>%
    mutate(pvalue1=case_when((pvalue1<0.00001) ~ "<0.0001",
                             (pvalue1<0.001)~ "<0.001")) 
  
  pvalues_smooth_SB_main_df$pvalue1 <- (ifelse(is.na(pvalues_smooth_SB_main_df$pvalue1), pvalues_smooth_SB_main_df$pvalue, pvalues_smooth_SB_main_df$pvalue1))
  
  pvalues_smooth_SB_main_gt <- pvalues_smooth_SB_main_df %>%
    select(-one_of('pvalue')) %>%
   rename("p-value"="pvalue1") %>%
    gt()%>% 
     tab_header(title=md(gt::html("**Table 6.B : Stillbirth GAM (model 3.1)**")), 
              subtitle = "smooth variables") %>%
  tab_options(table.width = pct(12), data_row.padding = px(1),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14,
              source_notes.font.size = 12)
  pvalues_smooth_SB_main_gt
  
  pvalues_smooth_SB_main_gt_sv <- pvalues_smooth_SB_main_gt%>%
  gtsave(here("output/tables_paper", "pvalues_smooth_SB_main_gt.html"))
  pvalues_smooth_SB_main_gt_sv <- pvalues_smooth_SB_main_gt%>%
    gtsave(here("output/tables_paper", "pvalues_smooth_SB_main_gt.docx"))
```


# Preterm birth (without adjusting for birthweight)
```{r echo=FALSE}
   m_PTB3_no_crises <- bam(PTB ~s(mat_age) + birth_Y_M_num + s(month, bs="cc") + mean_ssep2 + mean_Alt_mean2+  parity_cat + sex +Urban3 + Language + mother_nationality_cat2, family="binomial", data=bevn_eco_in7) 
 summary(m_PTB3_no_crises) 
k.check(m_PTB3_no_crises)

   # m_PTB3_crises <- bam(PTB ~s(mat_age) + birth_Y_M_num + s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100+  parity_cat + sex +Urban3 + Language + mother_nationality_cat2 + civil_status3+  HW + GR_relativ_total + covid_hosp_relativ_total, family="binomial", data=bevn_eco_in7) 
       m_PTB3_crises_covid <- bam(PTB ~s(mat_age) + birth_Y_M_num + s(month, bs="cc") + mean_ssep2 + mean_Alt_mean2+  parity_cat + sex +Urban3 + Language + mother_nationality_cat2 +civil_status3 + covid_hosp_relativ_total, family="binomial", data=bevn_eco_in7) 
 summary(m_PTB3_crises_covid) 
 
      m_PTB3_crises_covid_cat <- bam(PTB ~s(mat_age) + birth_Y_M_num + s(month, bs="cc") + mean_ssep2 + mean_Alt_mean2+  parity_cat + sex +Urban3 + Language + mother_nationality_cat2 +civil_status3 + covid_hosp_relativ_total_cat, family="binomial", data=bevn_eco_in7)
      summary(m_PTB3_crises_covid_cat) 

      m_PTB3_crises_GR <- bam(PTB ~s(mat_age) + birth_Y_M_num + s(month, bs="cc") + mean_ssep2 + mean_Alt_mean2+  parity_cat + sex +Urban3 + Language + mother_nationality_cat2 +civil_status3 + GR_relativ_total, family="binomial", data=bevn_eco_in7) 
 summary(m_PTB3_crises_GR) 
 
 m_PTB3_crises_HW <- bam(PTB ~s(mat_age) + birth_Y_M_num + s(month, bs="cc") + mean_ssep2 + mean_Alt_mean2+  parity_cat + sex +Urban3 + Language + mother_nationality_cat2 +civil_status3+ HW , family="binomial", data=bevn_eco_in7)
  summary(m_PTB3_crises_HW) 
  
     m_PTB3_crises <- bam(PTB ~s(mat_age) + birth_Y_M_num + s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100+  parity_cat + sex +Urban3 + Language + mother_nationality_cat2 + civil_status3+  HW + GR_relativ_by_pregn_month  + covid_hosp_relativ_by_pregn_month, family="binomial", data=bevn_eco_in7)


    # extracting the plot information
plot_m_PTB_main_mat_age <- GAM_plot_function_binary(m_PTB3_crises, 1)
# plot_m_PTB_main_time <- GAM_plot_function_binary(m_PTB3_no_crises, 2)
plot_m_PTB_main_month <- GAM_plot_function_binary(m_PTB3_crises, 2)
# plot_m_PTB_main_sep <- GAM_plot_function_binary(m_PTB3_crises, 4)
# plot_m_PTB_main_altitude <- GAM_plot_function_binary(m_PTB3_crises, 5) 
```

## Graph maternal age X preterm birth

```{r}
plot_PTB_main_mat_age <- ggplot(data=plot_m_PTB_main_mat_age)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Maternal age (years)")+
  ylab("Preterm birth probability")+
  theme_bw()+
  coord_cartesian(ylim=c(0.05,0.2)) +
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(0,60,by=5),expand = c(0, 0)) +
  theme(axis.title.x = axis.title.x.position)
plot_PTB_main_mat_age
```


## Graph time variable X preterm birth

```{r}
x_date <-   bevn_eco_in7 %>% #careful, mayhave to change the dataset if I later work with smaller time ranges!
  select(birth_Y_M, birth_Y_M_num) %>%
  distinct(birth_Y_M, .keep_all = TRUE) %>%
  rename(x=birth_Y_M_num)

plot_data_PTB <- plot_m_PTB_main_time %>%
  mutate(x=round(x,0)) %>%
  left_join(x_date) %>%
  mutate(date_x= ymd(paste0(birth_Y_M,"-01")))
lim1 <- as.POSIXct(ymd("2007-01-01"))
lim2 <- as.POSIXct(ymd("2022-12-01"))

plot_PTB <- ggplot(data=plot_data_PTB)+
  geom_line(aes(x=as.POSIXct(date_x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=as.POSIXct(date_x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Timeline (years)")+
  ylab("Preterm birth probability")+
  coord_cartesian(ylim=c(0.005,0.1)) +
  scale_x_datetime( breaks = date_breaks("12 month"), 
                    labels = label_date_short(),
                    limits =c(as.POSIXct("2007-01-01"), max(lim2)),
                    expand = c(0,0)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
theme(axis.title.x = axis.title.x.position)
plot_PTB
```

## Graph seasonality X preterm birth 
```{r}
plot_PTB_main_seasonality <- ggplot(data=plot_m_PTB_main_month)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Month")+
  ylab("Preterm birth probability")+
  theme_bw()+
  coord_cartesian(ylim=c(0.05,0.2)) +
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(1,12,by=1),expand = c(0, 0)) +
  theme(axis.title.x = axis.title.x.position)
plot_PTB_main_seasonality
```

## Graph SSEP X preterm birth

```{r}
plot_PTB_main_SSEP <- ggplot(data=plot_m_PTB_main_sep)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("SSEP")+
  ylab("Preterm birth probability")+
  theme_bw()+
  coord_cartesian(ylim=c(0.05,0.14)) +
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(0,100,by=5),expand = c(0, 0)) +
  theme(axis.title.x = axis.title.x.position)
plot_PTB_main_SSEP
```

## Graph altitude X preterm birth

```{r}
plot_PTB_main_altitude <- ggplot(data=plot_m_PTB_main_altitude)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Altitude (MASL)")+
  ylab("Preterm birth probability")+
  theme_bw()+
  coord_cartesian(ylim=c(0.05,0.14)) +
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(0,2000,by=200),expand = c(0, 0)) +
  theme(axis.title.x = axis.title.x.position)
plot_PTB_main_altitude
```

## Table summarizing the preterm birth outcome model

```{r}
  OR <- exp(coef(m_PTB3_crises))
  beta <- coef(m_PTB3_crises)
  Vb <- vcov(m_PTB3_crises , unconditional = TRUE)
  se <- sqrt(diag(Vb))
  lci <- exp(beta-1.96*se)
  uci <- exp(beta+1.96*se)
  d <- abs(beta)/1.81
  my.ci <- data.frame(cbind(OR, lci, uci, d))
  tab_PTB_crises <- round(head(my.ci, 20), 2)
```

```{r}
tab_PTB_crises['Variable'] <- c("Intercept", 
                                "Time (by month)", "SSEP (/10 points)",
                            "Altitude (/100m)",
                                "Parity (ref: 1)", " ", " ", 
                              "Sex (ref: male)", "Urban (ref: rural)",
                              "Language region (ref: German)", " ", 
                              "Maternal nationality (ref: Swiss)", " ", " ",
                              " ", " ",
                              "Civil status (ref: married)",
                              "Heatwave (ref: 0)", "Great Recession (continuous)",
                              "COVID (continuous)")

    tab_PTB_crises['Category'] <- c(" ", 
                                    " ", " "," ",
                                    "2", "3", ">3", "Female", "Urban",
                                    "French", "Italian", 
                            "Africa", "Asia", "Europe", "Northern America",
                            "Southern/Central America", "Single", "1", "","")
    tab_PTB_crises<-tab_PTB_crises[, c('Variable', "Category", "OR", "lci","uci", "d")]

tab_PTB_main_gt<- tab_PTB_crises %>%
  gt()%>%
  tab_header(title=md(gt::html("**Table 5.A : Association between the risk of preterm birth and <br> neonatal, maternal and ecological factors from a GAM (model 2.1)**")),
               subtitle = "linear categorical variables") %>%
  tab_spanner(label = "95% CI", columns = c(lci, uci)) %>%
  tab_style(
    style = list(
          cell_fill(color = "#E0E0E0")
        ),
        locations = cells_body(rows=c(2, 4, 8, 10,11,
                                      17,19)))%>%
    tab_style(
    style = list(
     cell_fill(color = "#F2F0F0")),
        locations = cells_body(rows=c(3, 5, 6, 7, 9, 12, 13,
                                      14,15,16,18,20))) %>%
   tab_options(table.width = pct(35), data_row.padding = px(1),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14,
              source_notes.font.size = 12) %>%
  tab_source_note(source_note = "n=1,263,853")
tab_PTB_main_gt

PTB_estimates_main_gt <- tab_PTB_main_gt%>%
  gtsave(here("output/tables_paper", "PTB_estimates_main.html"))
PTB_estimates_main_gt <- tab_PTB_main_gt%>%
  gtsave(here("output/tables_paper", "PTB_estimates_main.docx"))

# # same table with bold for the "significant" results
#   PTB_full_gt_bold <- tab_PTB_full %>%
#   gt()%>%
#   tab_header(title="Preterm birth GAM") %>%
#   tab_spanner(label = "95% CI", columns = c(lci, uci)) %>%
#   tab_style(
#     style = list(
#           cell_fill(color = "#E0E0E0")
#         ),
#         locations = cells_body(rows=c(2, 3, 4, 6, 9, 10, 11,12,13,15,17 )))%>%
#     tab_style(
#     style = list(
#      cell_fill(color = "#F2F0F0")),
#         locations = cells_body(rows=c(5, 7, 8, 14,16,18))) %>%
#     tab_style(
#     style = list(
#       cell_text(weight = "bold")
#       ),
#     locations = cells_body(rows=c(2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 13), columns=c(3:5)
#     ))
# PTB_full_gt_bold
# 
# PTB_estimates_whole_model_gt_bold <- PTB_full_gt_bold%>%
#   gtsave(here("output/tables_paper", "PTB_estimates_whole_model_gt_bold.html"))
# PTB_estimates_whole_model_gt <- PTB_full_gt%>%
#   gtsave(here("output/tables_paper", "PTB_estimates_whole_model_gt_bold.docx"))
```

## Table summarizing smooth term pvalues of the PTB model

```{r}
  pvalues_smooth_PTB_main = summary(m_PTB3_crises)
  pvalues_smooth_PTB_main <- pvalues_smooth_PTB_main$s.table[,4]
  pvalues_smooth_PTB_main <- format(pvalues_smooth_PTB_main, scientific=FALSE)
  
  pvalues_smooth_PTB_main_df <- data.frame(pvalues_smooth_PTB_main) %>%
    dplyr::mutate(Variable=c("Maternal age", "Seasonality")) %>%
    rename(c(pvalue=(pvalues_smooth_PTB_main)))%>%
    mutate(pvalue=as.numeric(pvalue)) %>%
    mutate(pvalue1=pvalue) 
  
  pvalues_smooth_PTB_main_df$pvalue <-  format(round(pvalues_smooth_PTB_main_df$pvalue, digits=3), nsmall=2)
  
  pvalues_smooth_PTB_main_df <- pvalues_smooth_PTB_main_df %>%
    mutate(pvalue1=case_when((pvalue1<0.00001) ~ "<0.0001",
                             (pvalue1<0.001)~ "<0.001")) 
  
  pvalues_smooth_PTB_main_df$pvalue1 <- (ifelse(is.na(pvalues_smooth_PTB_main_df$pvalue1),                                                            pvalues_smooth_PTB_main_df$pvalue,  
                                                 pvalues_smooth_PTB_main_df$pvalue1))
  
  pvalues_smooth_PTB_main_gt <- pvalues_smooth_PTB_main_df %>%
    select(-one_of('pvalue')) %>%
      rename("p-value"="pvalue1") %>%
      gt()%>% 
  tab_header(title=md(gt::html("**Table 5.B : Preterm birth GAM (model 2.1)**")), 
              subtitle = "smooth variables") %>%
  tab_options(table.width = pct(10), data_row.padding = px(1),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14,
              source_notes.font.size = 12)
  pvalues_smooth_PTB_main_gt
  
  pvalues_smooth_PTB_main_gt_sv <- pvalues_smooth_PTB_main_gt%>%
    gtsave(here("output/tables_paper", "PTB_full_smooth_pvalues_main.html")) 
  pvalues_smooth_PTB_main_gt_sv <- pvalues_smooth_PTB_main_gt%>%
    gtsave(here("output/tables_paper", "PTB_full_smooth_pvalues_main.docx"))
```
