---
title: "GAM all variables different outcomes. Flu pandemic instead of Great Recession"
author: "Mathilde Le Vu"
date:  "`r Sys.Date()`"
html_document: 
output:
  rmdformats::robobook:
    code_folding: show
    self_contained: true
    highlight: pygments
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Birthweight

```{r}
 m_BW_flu <- bam(BW ~ s(mat_age) + birth_Y_M_num+  s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100 + parity_cat + sex + Urban3 + Language + mother_nationality_cat2  +civil_status3+ HW + flu_relativ_by_pregn_month + covid_hosp_relativ_by_pregn_month, data=bevn_eco_in7) 

  summary(m_BW_flu)
k.check(m_BW_flu)
cor(bevn_eco_in7$birth_Y_M_num, bevn_eco_in7$flu_relativ_total)

# extracting the plot information
plot_m_BW_mat_age_flu <- GAM_plot_function_continuous(m_BW_flu, 1) # mat age
plot_m_BW_month_flu <- GAM_plot_function_continuous(m_BW_flu, 2) #seasonality
```

## Graph maternal age variable X BW (not adj for GA)

```{r}
plot_BW_mat_age_flu <- ggplot(data=plot_m_BW_mat_age_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Maternal age (years)")+
  ylab("Birthweight (g)")+
  coord_cartesian(ylim=c(3160,3380)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(0,60,by=5),expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(0,4000,by=50)) +
theme(axis.title.x = axis.title.x.position)
plot_BW_mat_age_flu
```

## Graph seasonality X birthweight (not adj for GA)

```{r}
plot_BW_month_flu <- ggplot(data=plot_m_BW_month_flu)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Month")+
  ylab("Birthweight (g)")+
  coord_cartesian(ylim=c(3160,3380)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(1,12,by=1),expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(0,4000,by=50)) +
theme(axis.title.x = axis.title.x.position)
plot_BW_month_flu
```

## Table summarizing the birthweight outcome model (not adj for GA)
### Categorical and smooth variables together
### Without the intercept
```{r}
beta <- coef(m_BW_flu)
Vb <- vcov(m_BW_flu, unconditional = TRUE)
se <- sqrt(diag(Vb))
n <- 1263853 #to check
d <- (abs(beta)/(sqrt(n)*se))
my.ci <- data.frame(cbind(beta, lci = beta-1.96*se, uci = beta + 1.96*se, d))
tab_BW_bam <- format(round((my.ci[2:20,]), 2), nsmall=2)

tab_BW_bam['Variable'] <- c("Time (by month)", "SSEP (/10 points)",
                            "Altitude (/100m)",
                            "Parity (ref: 1)", " ", " ", 
                            "Sex (ref: male)", "Urban (ref: rural)",
                            "Language region (ref: German)", " ", 
                            "Maternal nationality (ref: Swiss)", " ", " ",
                            " ", " ",
                            "Civil status (ref: married)",
                            "Heatwave (ref: 0)",
                            "Flu pandemic (continuous)",
                            "COVID (continuous)")
tab_BW_bam['Category'] <- c(" "," "," ",
                            "2", "3", ">3", "Female", "Urban", "French", "Italian", 
                            "Africa", "Asia", "Europe", "Northern America",
                            "Southern/Central America", "Single", "1", "","")
tab_BW_bam<-tab_BW_bam[, c('Variable', "Category", "beta", "lci","uci", "d")]
tab_BW_bam <-tab_BW_bam %>%
  mutate(beta=as.character(beta),
         lci=as.character(lci),
         uci=as.character(uci),
         d=as.character(d))

pvalues_smooth_BW_main = summary(m_BW_flu)
pvalues_smooth_BW_main <- pvalues_smooth_BW_main$s.table[,4]
pvalues_smooth_BW_main <- format(pvalues_smooth_BW_main, scientific=FALSE)

pvalues_smooth_BW_main_df <- data.frame(pvalues_smooth_BW_main) %>%
  dplyr::mutate(Variable=c("Maternal age (years)", "Seasonality (month)")) %>%
  rename(c(pvalue=(pvalues_smooth_BW_main)))%>%
  mutate(pvalue=as.numeric(pvalue)) %>%
  mutate(pvalue1=pvalue) %>%
  add_column(beta="")%>%
  add_column(Category="")%>%
  add_column(lci="") %>%
  add_column(uci="")

pvalues_smooth_BW_main_df$pvalue <-  format(round(pvalues_smooth_BW_main_df$pvalue, digits=2), nsmall=2)

pvalues_smooth_BW_main_df <- pvalues_smooth_BW_main_df %>%
  mutate(pvalue1=case_when((pvalue1<0.00001) ~ "<0.0001",
                           (pvalue1<0.001)~ "<0.001",
                           (pvalue1<0.01)~ "<0.01")) 

pvalues_smooth_BW_main_df$pvalue1 <- (ifelse(is.na(pvalues_smooth_BW_main_df$pvalue1), 
                                             pvalues_smooth_BW_main_df$pvalue, pvalues_smooth_BW_main_df$pvalue1))
pvalues_smooth_BW_main_df <- pvalues_smooth_BW_main_df%>%
  rename("d"="pvalue1") %>%
  select(-one_of('pvalue')) 
rowinfo = c("Smooth variables", "p-value","", "", "", "")
ow <- rbind(rowinfo,pvalues_smooth_BW_main_df)

BW <- rbind(tab_BW_bam, ow)

tab_BW_bam_flu_gt <- BW %>%
  gt()%>%
  # tab_header(title=md(gt::html("**Association between birthweight and <br> neonatal, maternal and ecological factors from a GAM (model 1.2)**"))) %>%
  tab_spanner(label = "95% CI (g)", columns = c(lci, uci)) %>%
  tab_style(
    style = list(
      cell_fill(color = "#E0E0E0")
    ),
    locations = cells_body(rows=c(1, 3, 7,9,10,16,18,21)))%>%
  tab_style(
    style = list(
      cell_fill(color = "#F2F0F0")),
    locations = cells_body(rows=c(2,4,5,6,8,11:15,17,19,22))) %>%
  tab_options(table.width = pct(30), data_row.padding = px(1),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14,
              source_notes.font.size = 12) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(rows = 20)) %>%
  tab_source_note(source_note = "n=1,263,853")
tab_BW_bam_flu_gt

BW_estimates_flu_gt <- tab_BW_bam_flu_gt %>%
  gtsave(here("output/tables_for_paper/suppl_material", "BW_estimates_flu_gt.html"))
BW_estimates_flu_gt <- tab_BW_bam_flu_gt %>%
  gtsave(here("output/tables_for_paper/suppl_material", "BW_estimates_flu_gt.docx"))
```

# Stillbirth- simple model, without adjusting for GA

```{r}
m_SB_crises_flu <- bam(stillbirth~ s(mat_age) + birth_Y_M_num+ s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100 + sex + Urban3 + Language + mother_nationality_cat1 + civil_status3 + HW + flu_relativ_by_pregn_month + covid_hosp_relativ_by_pregn_month, family="binomial", data=bevn_eco_in6)

  k.check(m_SB_crises_flu) 
  summary(m_SB_crises_flu)

plot_m_SB_flu_mat_age <- GAM_plot_function_binary(m_SB_crises_flu, 1)
plot_m_SB_flu_month <- GAM_plot_function_binary(m_SB_crises_flu, 2)

concurvity(m_SB_crises_flu, full = TRUE)
```

## Graph maternal age X Stillbirth

```{r}
plot_SB_flu_mat_age <- ggplot(data=plot_m_SB_flu_mat_age)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Maternal age (years)")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.0005,0.01)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom")+
  scale_x_continuous(breaks=seq(0,60,by=5),expand = c(0, 0)) +
theme(axis.title.x = axis.title.x.position)
plot_SB_flu_mat_age
```

## Graph seasonality X Stillbirth

```{r}
plot_SB_flu_month <- ggplot(data=plot_m_SB_flu_month)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Month")+
  ylab("Stillbirth probability")+
  coord_cartesian(ylim=c(0.0005,0.01)) +
  theme_bw()+
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom")+
  scale_x_continuous(breaks=seq(1,12,by=1),expand = c(0, 0)) +
theme(axis.title.x = axis.title.x.position)
plot_SB_flu_month
```

## Table summarizing the stillbirth outcome model
## Without the intercept
## Catgorical and smooth variables together
```{r}
  OR <- exp(coef(m_SB_crises_flu))
  beta <- coef(m_SB_crises_flu)
  Vb <- vcov(m_SB_crises_flu , unconditional = TRUE)
  se <- sqrt(diag(Vb))
  lci <- exp(beta-1.96*se)
  uci <- exp(beta+1.96*se)
  d <- abs(beta)/1.81
  my.ci <- data.frame(cbind(OR, lci, uci, d))
  tab_SB_main <- format(round((my.ci[2:13,]), 2), nsmall=2)
  
  tab_SB_main <-tab_SB_main %>%
  mutate(OR=as.character(OR),
         lci=as.character(lci),
         uci=as.character(uci),
         d=as.character(d))
  
tab_SB_main['Variable'] <- c("Time (by month)","SSEP (/10 points)",
                            "Altitude (/100m)",
                             "Sex (ref: male)", "Urban (ref: rural)",
 "Language region (ref: German)", " ", 
  "Maternal nationality (ref: Swiss)", 
 "Civil status (ref: married)",
   "Heatwave (ref: 0)", "Flu pandemic (continuous)","COVID (continuous)")

    tab_SB_main['Category'] <- c(" "," "," ",
                                 "Female", "Urban", "French", "Italian", "Not Swiss", "Single", "1", "","")
    tab_SB_main<-tab_SB_main[, c('Variable', "Category", "OR", "lci","uci", "d")]


pvalues_smooth_SB_main = summary(m_SB_crises_flu)
pvalues_smooth_SB_main <- pvalues_smooth_SB_main$s.table[,4]
pvalues_smooth_SB_main <- format(pvalues_smooth_SB_main, scientific=FALSE)

pvalues_smooth_SB_main_df <- data.frame(pvalues_smooth_SB_main) %>%
  dplyr::mutate(Variable=c("Maternal age (years)", "Seasonality (month)")) %>%
  rename(c(pvalue=(pvalues_smooth_SB_main)))%>%
  mutate(pvalue=as.numeric(pvalue)) %>%
  mutate(pvalue1=pvalue) %>%
  add_column(OR="")%>%
  add_column(Category="")%>%
  add_column(lci="") %>%
  add_column(uci="")

pvalues_smooth_SB_main_df$pvalue <-  format(round(pvalues_smooth_SB_main_df$pvalue, digits=2), nsmall=2)

pvalues_smooth_SB_main_df <- pvalues_smooth_SB_main_df %>%
  mutate(pvalue1=case_when((pvalue1<0.00001) ~ "<0.0001",
                           (pvalue1<0.001)~ "<0.001",
                           (pvalue1<0.01)~ "<0.01")) 

pvalues_smooth_SB_main_df$pvalue1 <- (ifelse(is.na(pvalues_smooth_SB_main_df$pvalue1), 
                                             pvalues_smooth_SB_main_df$pvalue, pvalues_smooth_SB_main_df$pvalue1))
pvalues_smooth_SB_main_df <- pvalues_smooth_SB_main_df%>%
  rename("d"="pvalue1") %>%
  select(-one_of('pvalue')) 
rowinfo = c("Smooth variables", "p-value","", "", "", "")
ow <- rbind(rowinfo,pvalues_smooth_SB_main_df)

SB <- rbind(tab_SB_main, ow)

estimates_smooth_SB_flu_gt <- SB %>%
  gt()%>%
  # tab_header(title=md(gt::html("**Association between the risk of stillbirth and <br> neonatal, maternal and ecological factors from a GAM (model 3.2)**"))) %>%
  tab_spanner(label = "95% CI", columns = c(lci, uci)) %>%
 tab_style(
    style = list(
          cell_fill(color = "#E0E0E0")
        ),
        locations = cells_body(rows=c(1,3,5,8,10,12,15)))%>%
    tab_style(
    style = list(
     cell_fill(color = "#F2F0F0")),
        locations = cells_body(rows=c(2,4,6,7,9,11,14))) %>%
  tab_options(table.width = pct(30), data_row.padding = px(1),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14,
              source_notes.font.size = 12) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(rows = 13)) %>%
  tab_source_note(source_note = "n=1,270,114")
estimates_smooth_SB_flu_gt

  pvalues_smooth_SB_main_gt_sv <- estimates_smooth_SB_flu_gt%>%
  gtsave(here("output/tables_for_paper/suppl_material", "estimates_SB_flu_gt.html"))
  pvalues_smooth_SB_main_gt_sv <- estimates_smooth_SB_flu_gt%>%
    gtsave(here("output/tables_for_paper/suppl_material", "estimates_SB_flu_gt.docx"))
```

# Preterm birth (without adjusting for birthweight)
```{r echo=FALSE}
   m_PTB3_flu <- bam(PTB ~s(mat_age) + birth_Y_M_num + s(month, bs="cc") + mean_ssep2_by_10 + mean_Alt_mean2_by_100+  parity_cat + sex +Urban3 + Language + mother_nationality_cat2 + civil_status3+  HW + flu_relativ_by_pregn_month + covid_hosp_relativ_by_pregn_month, family="binomial", data=bevn_eco_in7)

summary(m_PTB3_flu) 
k.check(m_PTB3_flu)

plot_m_PTB_flu_mat_age <- GAM_plot_function_binary(m_PTB3_flu, 1)
plot_m_PTB_flu_month <- GAM_plot_function_binary(m_PTB3_flu, 2)
```

## Graph maternal age X preterm birth

```{r}
plot_PTB_flu_mat_age <- ggplot(data=plot_m_PTB_flu_mat_age)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Maternal age (years)")+
  ylab("Preterm birth probability")+
  theme_bw()+
  coord_cartesian(ylim=c(0.05,0.2)) +
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(0,60,by=5),expand = c(0, 0)) +
  theme(axis.title.x = axis.title.x.position)
plot_PTB_flu_mat_age
```

## Graph seasonality X preterm birth 
```{r}
plot_PTB_flu_seasonality <- ggplot(data=plot_m_PTB_flu_month)+
  geom_line(aes(x=(x),y=fit),lwd=lwdline, color=("black"))+
  geom_ribbon(aes(x=(x),ymin=CIl,ymax=CIu),alpha=0.15,lwd=lwdline, fill='black')+
  xlab("Month")+
  ylab("Preterm birth probability")+
  theme_bw()+
  coord_cartesian(ylim=c(0.05,0.2)) +
  theme(axis.text.y=element_text(color="black",size=size_axis),
        axis.text.x=element_text(color="black",size=size_axis,angle=45,hjust=1),
        axis.title=element_text(size=size_axis_title),
        legend.text=element_text(size=size_legend),
        legend.title=element_text(size=size_legend_title),
        legend.position="bottom") +
  scale_x_continuous(breaks=seq(1,12,by=1),expand = c(0, 0)) +
  theme(axis.title.x = axis.title.x.position)
plot_PTB_flu_seasonality
```

### Without the intercept
```{r}
  OR <- exp(coef(m_PTB3_flu))
  beta <- coef(m_PTB3_flu)
  Vb <- vcov(m_PTB3_flu , unconditional = TRUE)
  se <- sqrt(diag(Vb))
  lci <- exp(beta-1.96*se)
  uci <- exp(beta+1.96*se)
  d <- abs(beta)/1.81
  my.ci <- data.frame(cbind(OR, lci, uci, d))
  tab_PTB_bam <- format(round((my.ci[2:20,]), 2), nsmall=2)
  
  tab_PTB_crises <-tab_PTB_bam %>%
  mutate(OR=as.character(OR),
         lci=as.character(lci),
         uci=as.character(uci),
         d=as.character(d))
 
tab_PTB_crises['Variable'] <- c("Time (by month)","SSEP (/10 points)",
                            "Altitude (/100m)","Parity (ref: 1)", " ", " ", 
                             "Sex (ref: male)", "Urban (ref: rural)",
                            "Language region (ref: German)", " ", 
                            "Maternal nationality (ref: Swiss)", " ", " ",
                            " ", " ",
                            "Civil status (ref: married)",
                            "Heatwave (ref: 0)", "Flu pandemic (continuous)",
                            "COVID (continuous)")

    tab_PTB_crises['Category'] <- c(" "," "," ",
                                 "2", "3", ">3", "Female",
                                 "Urban", "French", "Italian",
                                  "Africa", "Asia", "Europe", "Northern America",
                            "Southern/Central America",
                            "Single", "1", "","")
    tab_PTB_crises<-tab_PTB_crises[, c('Variable', "Category", "OR", "lci","uci", "d")]


pvalues_smooth_PTB_main = summary(m_PTB3_flu)
pvalues_smooth_PTB_main <- pvalues_smooth_PTB_main$s.table[,4]
pvalues_smooth_PTB_main <- format(pvalues_smooth_PTB_main, scientific=FALSE)

pvalues_smooth_PTB_main_df <- data.frame(pvalues_smooth_PTB_main) %>%
  dplyr::mutate(Variable=c("Maternal age (years)", "Seasonality (month)")) %>%
  rename(c(pvalue=(pvalues_smooth_PTB_main)))%>%
  mutate(pvalue=as.numeric(pvalue)) %>%
  mutate(pvalue1=pvalue) %>%
  add_column(OR="")%>%
  add_column(Category="")%>%
  add_column(lci="") %>%
  add_column(uci="")

pvalues_smooth_PTB_main_df$pvalue <-  format(round(pvalues_smooth_PTB_main_df$pvalue, digits=2), nsmall=2)

pvalues_smooth_PTB_main_df <- pvalues_smooth_PTB_main_df %>%
  mutate(pvalue1=case_when((pvalue1<0.00001) ~ "<0.0001",
                           (pvalue1<0.001)~ "<0.001",
                           (pvalue1<0.01)~ "<0.01")) 

pvalues_smooth_PTB_main_df$pvalue1 <- (ifelse(is.na(pvalues_smooth_PTB_main_df$pvalue1), 
                                             pvalues_smooth_PTB_main_df$pvalue, pvalues_smooth_PTB_main_df$pvalue1))
pvalues_smooth_PTB_main_df <- pvalues_smooth_PTB_main_df%>%
  rename("d"="pvalue1") %>%
  select(-one_of('pvalue')) 
rowinfo = c("Smooth variables", "p-value","", "", "", "")
ow <- rbind(rowinfo,pvalues_smooth_PTB_main_df)

PTB <- rbind(tab_PTB_crises, ow)

PTB_flu_gt <- PTB %>%
  gt()%>%
  # tab_header(title=md(gt::html("**Table 3 : Association between the risk of preterm birth and <br> neonatal, maternal and ecological factors from a GAM (model 2.1)**"))) %>%
  tab_spanner(label = "95% CI", columns = c(lci, uci)) %>%
  tab_style(
    style = list(
          cell_fill(color = "#E0E0E0")
        ),
        locations = cells_body(rows=c(1, 3, 7, 9, 10, 16, 18, 21)))%>%
    tab_style(
    style = list(
     cell_fill(color = "#F2F0F0")),
        locations = cells_body(rows=c(2,4,5,6,8,11,12,
                                      13,14,15,17,19,22))) %>%
  tab_options(table.width = pct(30), data_row.padding = px(1),   table.font.size = 12,
              column_labels.font.weight = "bold",  row_group.font.weight  = "bold",
              heading.title.font.size = 14, heading.subtitle.font.size = 14,
              source_notes.font.size = 12) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(rows = 20)) %>%
  tab_source_note(source_note = "n=1,263,853")
PTB_flu_gt

PTB_estimates_flu_gt <- PTB_flu_gt%>%
  gtsave(here("output/tables_for_paper/suppl_material", "PTB_estimates_categ_and_smooth_flu_gt.html"))
PTB_estimates_flu_gt <- PTB_flu_gt%>%
  gtsave(here("output/tables_for_paper/suppl_material", "PTB_estimates_categ_and_smooth_flu_gt.docx"))
```