---
title: "Simple graphs/tables"
author: "Mathilde Le Vu"
date: '2022-07-10'
output: html_document
---

```{r setup, include=FALSE}
.libPaths(c("H:/Documents/R/win-library/4.1","C:/Program Files/R/R-4.1.2/library"))
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(dplyr)
```

## Geburtsstaat = State and world region of birth

```{r}
# State of birth in : Switzerland or Outside of Switzerland
  table(bevn_eco$Geburtsstaat_cat1, useNA = "always")
  round(prop.table(table(bevn_eco$Geburtsstaat_cat1, useNA="always"))*100,2)

#State of birth in : Switzerland, Europe, Africa, Americas, Asia, Oceania, other
table(bevn_eco$Geburtsstaat_cat2, useNA = "always")
round(prop.table(table(bevn_eco$Geburtsstaat_cat2, useNA="always"))*100,2)

#State of birth in : Switzerland, different parts of Europe, other
round(prop.table(table(bevn_eco$Geburtsstaat_cat3, useNA="always"))*100,2)
```

There are **148,335** births that occurred outside of Switzerland.

## Mutter: Staatsangehörigkeit = Nationality Mother

```{r}
summary(bevn_eco$Mutter..Staatsangehörigkeit)
table(bevn_eco$Mutter..Staatsangehörigkeit, useNA="always")

# Nationality of the mother in : Switzerland or Outside of Switzerland
  round(prop.table(table(bevn_eco$mother_nationality_cat1, useNA="always"))*100,2)
  
# Nationality of the mother in : Switzerland, Europe, Africa, Americas, Asia, Oceania, other
  round(prop.table(table(bevn_eco$mother_nationality_cat2, useNA="always"))*100,2)

#Nationality of the mother in : Switzerland, different parts of Europe, other
  round(prop.table(table(bevn_eco$mother_nationality_cat3, useNA="always"))*100,2)
```

## Mutter: Wohngemeinde / Wohnstaat = Place of residence Mother

1-6910 for commune if resident inside Switz <br> 8201-8703 if resident outside of Switz <br>

```{r}
#to check minimum and maximum
summary(bevn_eco$com)
head(bevn_eco$com,50)

# Place of residence of the mother in : inside or outside Switzerland
  round(prop.table(table(bevn_eco$mother_residence_cat1, useNA="always"))*100,2)
  table(bevn_eco$mother_residence_cat1, useNA="always")
```

## Mutter: ständig oder nicht-ständiger Wohnsitz = Residence of the mother

1=permanent resident, 2=non-permanent resident, 4=short stay, 9=domiciled abroad

```{r}
summary(bevn_eco$Mutter..ständig.oder.nicht.ständiger.Wohnsitz)
table(bevn_eco$Mutter..ständig.oder.nicht.ständiger.Wohnsitz, useNA = "always")
round(prop.table(table(bevn_eco$Mutter..ständig.oder.nicht.ständiger.Wohnsitz, useNA="always"))*100,2)
```
There are **183,076** women domiciled abroad

## Vater: Staatsangehörigkeit = Nationality father

See separate codebook. Expected: 8100-8703

```{r}
# categorizing nationality of the father in : inside or outside Switzerland
  round(prop.table(table(bevn_eco$father_nationality_cat1, useNA="always"))*100,2)
  table(bevn_eco$father_nationality_cat1, useNA="always")
```

## lebend geboren oder nicht = born alive or not

1=lifeborn, 2=stillborn

```{r}
table(bevn_eco$lebend.geboren.oder.nicht, useNA = "always")
round(prop.table(table(bevn_eco$lebend.geboren.oder.nicht, useNA="always"))*100,3)
```

## Gestational age

```{r}
## GA in weeks
summary(bevn_eco$GA_weeks)
```

## Kind: Grösse in Zentimeter = length at birth (cm)


```{r}
summary(bevn_eco$Kind..Grösse.in.Zentimeter)
table(bevn_eco$Kind..Grösse.in.Zentimeter, useNA = "always")
```

## Kind: Gewicht in Gramm = weight at birth (g)


```{r}
summary(bevn_eco$Kind..Gewicht.in.Gramm)

#BW categ. in LBW, "normal" (arbitrary decision) and high BW
table(bevn_eco$BW_cat, useNA="always")
round(prop.table(table(bevn_eco$BW_cat, useNA="always"))*100, 3)
```

There are **151,477** births with missing BW.


## Art der Geburt = number of babies 

1=singleton, 2=twins, 3=triplets, ..., 6=sextuplets and more <br>
```{r}
table(bevn_eco$Art.der.Geburt, useNA="always")
round(prop.table(table(bevn_eco$Art.der.Geburt, useNA="always"))*100,2)
##Single VS multiple pregnancies
table(bevn_eco$singleton_or_multiple)
round(prop.table(table(bevn_eco$singleton_or_multiple, useNA="always"))*100,2)
```

There are **92,864** multiple births.

## Mothers inside Switz without GMNDR: to check the number of missing
  table(bevn_eco$com1, bevn_eco$mother_residence_cat1, useNA = "always")
  round(prop.table(table(bevn_eco$com1, bevn_eco$mother_residence_cat1, useNA="always"), margin=2)*100,2)


# Simple tables

## Gestational age through the years
```{r}
#calculating median by year
 GA_median <- aggregate(GA_weeks ~ Ereignisjahr, data = bevn_eco, median) # from 2006 it was systematically collected
 GA_median

#same but using tidyverse
 gamedian <- bevn_eco %>%
   group_by(Ereignisjahr) %>%
     filter( !is.na(GA_weeks)) %>%
   summarise(medGA=format(median(GA_weeks),digits=5))%>%
 filter(Ereignisjahr>2005)
ungroup(gamedian)
gamedian

 #creating a function to calculate the mode of a variable
getmode <- function(v) {
   uniqv <- na.omit(unique(v))
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
# Calculate the GA mode through the years
ga_mode <- bevn_eco %>%
   group_by(Ereignisjahr) %>%
     filter( !is.na(GA_weeks)) %>%
   summarise(mode=format(getmode(GA_weeks), digits=5))%>%
 filter(Ereignisjahr>2005)
ungroup(ga_mode)
ga_mode


## GA frequency tables through the years
bevn_eco <- bevn_eco %>%
  mutate(GA_weeks_cat = cut (GA_weeks, breaks=c(16,24,30,34,39,44,46), include.lowest=TRUE))  
bevn_eco

bevn_eco1 <- bevn_eco %>%
  filter(!is.na(GA_weeks)) %>%
  filter(Ereignisjahr>2005)
bevn_eco1

GA_freq <- bevn_eco1 %>%
  group_by(Ereignisjahr) %>%
  ungroup(Ereignisjahr)

round(prop.table(table(GA_freq$GA_weeks_cat, GA_freq$Ereignisjahr, useNA="always"), margin=2)*100,2)
```


## Birthweight through the years

```{r}
BW_median2 <- aggregate(Kind..Gewicht.in.Gramm ~ Ereignisjahr, data = bevn_eco, median) 
BW_median2
plot(BW_median2)
```
Birthweight median slightly varies between 1987 and 2020, 3330-3350g.

## Length through the years

```{r}
BL_median <- aggregate(Kind..Grösse.in.Zentimeter ~ Ereignisjahr, data = bevn_eco, median) 
BL_median
```

Birthlength is robustly consistent at 50cm, 1987-2020.

## Sex % through the years

```{r}
tab1<- table(bevn_eco$Kind..Geschlecht, bevn_eco$Ereignisjahr)
tab1
round(prop.table(table(bevn_eco$Kind..Geschlecht, bevn_eco$Ereignisjahr), margin=2)*100,2)
```

## Stillbirth % through the years, their median GA and BW

```{r}
table(bevn_eco$lebend.geboren.oder.nicht, bevn_eco$Ereignisjahr, useNA="always")
round(prop.table(table(bevn_eco$lebend.geboren.oder.nicht, bevn_eco$Ereignisjahr), margin=2)*100,3)

#calculating median GA by year of birth, for stillborn
 GA_median_SB <- aggregate(GA_weeks ~ Ereignisjahr, data = subset(bevn_eco, lebend.geboren.oder.nicht==2 & Ereignisjahr >=2006), median) 
 GA_median_SB
  
 #calculating median GA by year of birth, for stillborn, with tidyverse
  GA_SB_Y <- bevn_eco %>%
  group_by(Ereignisjahr) %>%
  filter(lebend.geboren.oder.nicht==2) %>% 
  filter(Ereignisjahr>2005) %>% 
   filter(!is.na(GA_weeks)) %>% 
    summarise(medGA=format(median(GA_weeks),digits=5))   
  ungroup(GA_SB_Y) 
  GA_SB_Y 
  
#calculating mode GA by year of birth, for stillborn
  ga_y_mode <- bevn_eco %>%
   group_by(Ereignisjahr) %>%
     filter( !is.na(GA_weeks)) %>%
     filter(lebend.geboren.oder.nicht==2) %>% 
   summarise(mode=format(getmode(GA_weeks), digits=5))%>%
  filter(Ereignisjahr>2005)
  ungroup(ga_y_mode)
  ga_y_mode

#GA_frequency for stillbirths
 GA_SB <- bevn_eco %>%
  filter(Ereignisjahr>2005) %>% 
     filter(lebend.geboren.oder.nicht==2) 
  table(GA_SB$GA_weeks_cat)
  round(prop.table(table(GA_SB$GA_weeks_cat))*100,2)

#GA frequency for stillbirths, through the years
 GA_SB_Y_freq <- bevn_eco %>%
   group_by(Ereignisjahr) %>%
  filter(lebend.geboren.oder.nicht==2) %>% 
  filter(Ereignisjahr>2005) %>% 
 select(GA_weeks_cat)
  ungroup(GA_SB_Y_freq)
  GA_SB_Y_freq
  table(GA_SB_Y_freq$Ereignisjahr, GA_SB_Y_freq$GA_weeks_cat, useNA="always")
 round(prop.table(table(GA_SB_Y_freq$GA_weeks_cat, GA_SB_Y_freq$Ereignisjahr, useNA="always"), margin=2)*100,2)

 #calculating median BW for stillborn babies, by year
  BW_median_sb <- aggregate(Kind..Gewicht.in.Gramm ~ Ereignisjahr, data = subset(bevn_eco, lebend.geboren.oder.nicht==2), median) 
  BW_median_sb
  
 #calculating mode BW for stillborn babies, by year
  BW_y_mode <- bevn_eco %>%
   group_by(Ereignisjahr) %>%
     filter( !is.na(Kind..Gewicht.in.Gramm)) %>%
     filter(lebend.geboren.oder.nicht==2) %>% 
   summarise(mode=format(getmode(Kind..Gewicht.in.Gramm), digits=5))
  ungroup(BW_y_mode)
  BW_y_mode

  #BW frequency for stillbirths, through the years
  BW_SB_Y_freq <- bevn_eco %>%
   group_by(Ereignisjahr) %>%
  filter(lebend.geboren.oder.nicht==2) %>% 
   filter(!is.na(Kind..Gewicht.in.Gramm)) %>% 
  select(BW_cat) 
  ungroup(BW_SB_Y_freq)
 round(prop.table(table(BW_SB_Y_freq$BW_cat,BW_SB_Y_freq$Ereignisjahr), margin=2)*100,2)
```

Median GA varies betwen 27.71 and 31.14 weeks between 2006 and 2020.

## Age of the mother through the years

```{r}
AM_median <- aggregate(Mutter..Alter.in.erfüllten.Jahren ~ Ereignisjahr, data = bevn_eco, median)
AM_median
```

Maternal age varies increases between 28 and 32 yo between 1987 and 2020.


## Age difference between parents, through the years
```{r}
summary(bevn_eco$parent_age_diff)
agediff_y <- aggregate(parent_age_diff ~ Ereignisjahr, data = bevn_eco, median)
agediff_y
```


## Time variables

I created two variables for date : one combining month+year only, and another combining day+month+year.
I set up day to 1st of each month in order to have variable m-d-y, easier to work with.

```{r}
#month year
  tail(bevn_eco$birthdate3)
  head(bevn_eco$birthdate3)
  bevn_eco$birthdate3 <- as.factor(bevn_eco$birthdate3)

  #day month year
  summary(bevn_eco$birthdate2)
  tail(bevn_eco$birthdate2)
  head(bevn_eco$birthdate2)
```

# Simple plots

## BW or BL depending on GA and

2 different sets with either all birthweights/GA or birtsweights "normal" ]100;8000[ and GA >20 weeks
and with either all birthlengths or "normal" birthlengths ]10,60[ and GA >20 weeks

```{r}
plot(bevn_eco$GA_weeks,bevn_eco$Kind..Gewicht.in.Gramm) #BW and GA, all birthweights
plot(bevn_eco$GA_weeks, bevn_eco$Kind..Grösse.in.Zentimeter) #BL and GA, all birthlengths

BW_normal <- subset(bevn_eco, Kind..Gewicht.in.Gramm>100 & Kind..Gewicht.in.Gramm <8000 & GA_weeks>20)
summary(BW_normal$Kind..Gewicht.in.Gramm)
plot(BW_normal$GA_weeks, BW_normal$Kind..Gewicht.in.Gramm) #BW and GA, BW ]100;8000[

BL_normal <- subset(bevn_eco, Kind..Grösse.in.Zentimeter>10 & Kind..Grösse.in.Zentimeter <60  & GA_weeks>20)
summary(BL_normal$Kind..Grösse.in.Zentimeter)
plot(BL_normal$GA_weeks, BL_normal$Kind..Grösse.in.Zentimeter) #BL and GA, BL ]10;60[

BW_BL_normal <- subset(bevn_eco, Kind..Grösse.in.Zentimeter>10 & Kind..Grösse.in.Zentimeter <60 & Kind..Gewicht.in.Gramm>100 & Kind..Gewicht.in.Gramm <8000  & GA_weeks>20)
plot(BW_BL_normal$Kind..Gewicht.in.Gramm,BW_BL_normal$Kind..Grösse.in.Zentimeter) #BW and BL
```




# UNIVARIATE ANALYSIS

## BIRTHWEIGHT

### Birthweight change through the years: Simple model

```{r BW through years}
##boxplot(bevn_eco$Ereignisjahr, bevn_eco$Kind..Gewicht.in.Gramm) ##doesnt work
m_BW_years <- lm(Kind..Gewicht.in.Gramm~Ereignisjahr, data=bevn_eco)
summary(m_BW_years)

bevn_eco$TimeInterval <- cut(bevn_eco$Ereignisjahr, breaks=c(1989, 1996, 2003, 2010, 2017))
boxplot(Kind..Gewicht.in.Gramm~TimeInterval, data=bevn_eco)
meanBW <- mean(bevn_eco$Kind..Gewicht.in.Gramm)

# BW_time3 <- lm(Kind..Gewicht.in.Gramm~year+month, data=bevn_eco) ##doesnt work
## m_BW_time3 <- lm(Kind..Gewicht.in.Gramm~ factor(Ereignisjahr)+factor(Ereignismonat), data=bevn_eco) ##to not interpret too much
summary(m_BW_time3)

m_BW_time2 <- lm(Kind..Gewicht.in.Gramm~birthdate2, data=bevn_eco)
summary(m_BW_time2)
```
### BW related to sex
```{r}
m_BW_sex <- lm(Kind..Gewicht.in.Gramm~Kind..Geschlecht, data=bevn_eco)
summary(m_BW_sex) #female is the reference
table(bevn_eco$Kind..Geschlecht)
```
Males are around 134g heavier than females, and this is highly significant

### BW related to maternal age
```{r}
m_BW_mat_age <- lm(Kind..Gewicht.in.Gramm~Mutter..Alter.in.erfüllten.Jahren, data=bevn_eco)
summary(m_BW_mat_age)
```
BW decreases significantly when maternal age increases.

### BW related to GA
```{r}
m_BW_GA <- lm(Kind..Gewicht.in.Gramm ~GA_weeks, data=bevn_eco)
summary(m_BW_GA)
```
BW increases with GA : each GA weeks is associated with an increase of 187g. 

## STILLBIRTH

### stillbirth related to maternal age
```{r}
m_SB_mat_age <- glm(lebend.geboren.oder.nicht~Mutter..Alter.in.erfüllten.Jahren, data=bevn_eco)
summary(m_SB_mat_age)

exp(coef(summary(m_SB_mat_age)))[,"Estimate"]
#exp(confint(m_SB_mat_age))  doesnt work 
```



## MULTIVARIATE
```{r}
m_BW <- lm(Kind..Gewicht.in.Gramm ~ GA_weeks + birthdate2 + Mutter..Alter.in.erfüllten.Jahren + Kind..Rang.in.der.aktuellen.Ehe + Kind..Geschlecht, data=bevn_eco)

summary(m_BW)


m_BW_inclusions <- lm(Kind..Gewicht.in.Gramm ~ GA_weeks + birthdate2 + Mutter..Alter.in.erfüllten.Jahren + Kind..Rang.in.der.aktuellen.Ehe + Kind..Geschlecht, data=bevn_eco_in8)

summary(m_BW_inclusions) 
```

